\documentclass[12pt]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}

\def\univname{}
\def\coursenum{}
\def\coursename{Differential Topology}
\def\professor{}
\def\student{Aryaman Maithani}
\def\semesteryear{Spring 2022}
\def\imagename{../icon.pdf}		  
\def\scalesize{2}
\usepackage{../aryaman}
\setcounter{tocdepth}{2}

\newcommand{\opsub}{\subset_{\operatorname{op}}}
\newcommand{\T}{\mathscr{T}}
\DeclareMathOperator{\Alt}{Alt}

\newcommand{\trans}{\mathrel{\text{\tpitchfork}}}
\makeatletter
\newcommand{\tpitchfork}{%
  \vbox{
    \baselineskip\z@skip
    \lineskip-.52ex
    \lineskiplimit\maxdimen
    \m@th
    \ialign{##\crcr\hidewidth\smash{$-$}\hidewidth\crcr$\pitchfork$\crcr}
  }%
}
\makeatother

\begin{document}

\pagenumbering{Alph}
\coverpage
\thispagestyle{empty}
\updated{\today}
\thispagestyle{empty}
% \setcounter{tocdepth}{1}
\pagenumbering{arabic}
\tableofcontents
\pagestyle{fancy}
% \setcounter{page}{1}
\setcounter{section}{-1}

\section{Preface}

I am making this while I study \emph{Differential Topology} by Victor Guillemin and Alan Pollack. These notes will likely not be helpful to anyone who is looking to learn this material from scratch. I am just going to be noting down the theorems and definitions from the book, assuming the definitions and notations I want to assume. I also skip proofs.

\textbf{Notations}
\begin{enumerate}
	\item ``$U \opsub X$'' stands for ``$U$ is a nonempty open subset of $X$''.
	\item Given a function $f : X \to \mathbb{R}^{m}$, we can write $f = (f_{1}, \ldots, f_{m})$ for functions $f_{i} : X \to \mathbb{R}$ ($i = 1, \ldots, m$). These $f_{i}$ will be referred to as \deff{component functions (of $f$)}.
	\item $S^{k} \subset \mathbb{R}^{k + 1}$ is the unit sphere.
	\item $B_{r}(p)$ will denote the open ball of radius $r$ around the point $p$. The ambient metric space will be clear from context.
	\item Given a function $T : V \to W$, $\im(T)$ denotes the image of $T$.
	\item $\mathbb{H}^{k}$ denotes the upper half-space in $\mathbb{R}^{k}$, i.e.,
	\begin{equation*} 
		\mathbb{H}^{k} \vcentcolon= \{(x_{1}, \ldots, x_{k}) \in \mathbb{R}^{k} : x_{k} \ge 0\}.
	\end{equation*}
	$\partial \mathbb{H}^{k}$ consists of those points in $\mathbb{R}^{k}$ with final coordinate $0$.
	\item For $n \in \mathbb{N}$, $[n]$ will denote the set $\{1, \ldots, n\}$.
\end{enumerate}

\begin{thm}[Invariance of Domain] \label{thm:invariance-of-domain}
	If $U \subset \mathbb{R}^{n}$ is open and $f : U \to \mathbb{R}^{n}$ is an injective continuous function, then $f(U)$ is open in $\mathbb{R}^{n}$.
\end{thm}

\begin{cor}
	Let $U \opsub \mathbb{R}^{n}$ and $V \opsub \mathbb{R}^{m}$. If $U$ and $V$ are homeomorphic, then $n = m$. In particular, $\mathbb{R}^{n}$ and $\mathbb{R}^{m}$ are not homeomorphic for $n \neq m$.
\end{cor}
Note that our notation forces $U$ and $V$ above to be nonempty.
\begin{proof} 
	Suppose $n \neq m$. Without loss of generality, $m > n$. Let $f : V \to U$ be a homeomorphism. Let $g : U \to \mathbb{R}^{m}$ denote the restriction of the inclusion $\mathbb{R}^{n} \into \mathbb{R}^{m}$ given by $\mathbf{x} \mapsto (\mathbf{x}, \mathbf{0})$. \newline
	Thus, $g \circ f : V \to \mathbb{R}^{m}$ is an injective continuous function mapping $V$ onto $g(U) \subset \mathbb{R}^{m}$. But $g(U)$ is not open in $\mathbb{R}^{m}$, contradicting \mynameref{thm:invariance-of-domain}.
\end{proof}

\begin{cor} \label{cor:boundary-Hk-intrinsic}
	Let $x, y \in \mathbb{H}^{k}$. Let $U$ and $V$ be open neighbourhoods of $x$ and $y$ in $\mathbb{H}^{k}$ respectively. If $U$ and $V$ are homeomorphic, then either both $x$ and $y$ belong to $\partial \mathbb{H}^{k}$ or neither does.
\end{cor}
The above corollary is useful later in developing a consistent definition of ``boundary''. It says that the boundary points have topologically different neighbourhoods.
\begin{proof} 
	Suppose that the statement were false. Without loss of generality, $y \in \partial \mathbb{H}^{k}$ and $x \notin \mathbb{H}^{k}$. Note that $f$ restricted to a subset of $U$ is again homeomorphism onto its image. Thus, by shrinking $U$, we may assume that $U$ is an open ball in $\mathbb{R}^{k}$ contained in $\mathbb{H}^{k}$. 

	Let $f : U \to V$ be a homeomorphism. Pick $r > 0$ such that $B_{r}(y) \cap \mathbb{H}^{k} \subset V$. (Here, $B_{r}(y)$ denotes the ball in $\mathbb{R}^{k}$.) 

	Let $V' \vcentcolon= B_{r}(y) \cap \mathbb{H}^{k}$. Note that $V'$ is not open in $\mathbb{R}^{k}$. But $f$ restricted to $f^{-1}(V')$ is an injective continuous map from an open subset of $\mathbb{R}^{k}$ onto the non-open subset $V'$, contradicting \mynameref{thm:invariance-of-domain}.
\end{proof}

\input{sections/01-manifolds-smooth-maps}

\section{Transversality and Intersection}
\subsection{Manifolds with Boundary}

\begin{defn}
	A subset $X \subset \mathbb{R}^{N}$ is a \deff{$k$-dimensional manifold with boundary} if every point of $X$ possesses a (relative) neighbourhood diffeomorphic to an open subset of $\mathbb{H}^{k}$. A \deff{local parametrisation} is defined similarly as before.

	The \deff{boundary of $X$}, denoted $\partial X$, consists of those points that belong to the image of $\partial \mathbb{H}^{k}$ under some local parametrisation. Its complement is called the \deff{interior of $X$}, denoted $\Int(X) = X \setminus \partial X$.
\end{defn}
Note that \Cref{cor:boundary-Hk-intrinsic} shows that if $x$ belongs to the image of $\partial \mathbb{H}^{k}$ under \emph{some} local parametrisation, then it does so under \emph{any}.

From now on, when we mean interior and boundary, we mean so in the manifold-with-boundary sense and not as a subset of $\mathbb{R}^{N}$. 

\begin{rem}
	Manifolds considered in the earlier chapter are also ``manifolds with boundary'' with $\partial X = \emptyset$.

	We shall continue to use the word ``manifold'' in the sense of the first chapter. For emphasis, we may sometimes refer to them as \emph{boundaryless}.
\end{rem}

\begin{ex} \label{ex:product-not-manifold-boundary}
	$X \vcentcolon= [0, 1]$ is a manifold with boundary. We have $\partial X = \{0, 1\}$. \newline
	Similarly, the closed disc $X' \vcentcolon= \overline{B_{1}(0)} \subset \mathbb{R}^{2}$ is a manifold with boundary. We have $\partial X' = S^{1}$.

	The product of two manifolds with boundary need not again be a manifold with boundary. For example, $[0, 1] \times [0, 1]$ is not a manifold with boundary (the corners are too pointy!).
\end{ex}

\begin{exe}
	Show that $\partial X$ is a closed subset of $X$.
\end{exe}

The failure in \Cref{ex:product-not-manifold-boundary} is essentially because $\mathbb{H}^{k} \times \mathbb{H}^{l}$ is not open in $\mathbb{H}^{k + l}$ (look at the case $k = l = 1$). However, $\mathbb{R}^{k} \times \mathbb{H}^{l}$ \emph{is} open in $\mathbb{H}^{k + l}$, giving us the next proposition. (We actually have $\mathbb{R}^{k} \times \mathbb{H}^{l} = \mathbb{H}^{k + l}$.)

\begin{prop}
	Let $X$ be a boundaryless manifold, and $Y$ be a manifold with boundary. \newline
	Then, $X \times Y$ is a manifold with boundary with
	\begin{equation*} 
		\partial(X \times Y) = X \times \partial Y \andd \dim(X \times Y) = \dim(X) + \dim(Y).
	\end{equation*}
\end{prop}

The earlier notions of derivatives and tangent spaces go as usual.

First, suppose that $U \opsub \mathbb{H}^{k}$ and $g : U \to \mathbb{R}^{l}$ is smooth. If $u$ is an interior point of $U$, then $dg_{u}$ is already defined. If $u \in \partial U$ (i.e., $u \in U \cap \partial \mathbb{H}$), then smoothness of $g$ allows an extension $\widetilde{g}$ to an open neighbourhood of $u$ in $\mathbb{R}^{k}$. $dg_{u}$ is then $d\widetilde{g}_{u} : \mathbb{R}^{k} \to \mathbb{R}^{l}$. \newline
Note that $dg_{u}$ is still a map from $\mathbb{R}^{k}$ to $\mathbb{R}^{l}$.

Now, if $X \subset \mathbb{R}^{N}$ is a manifold with boundary, and $x \in X$, then the \deff{tangent space} $T_{x}(X)$ is defined to be the image of any local parametrisation around $x$. As before, $T_{x}(X)$ is a $k$-dimensional (``concrete'') subspace, even when $x \in \partial X$. 

Lastly, given a smooth map $f : X \to Y$ between manifolds with boundary, the derivative may be defined as a linear transformation $df_{x} : T_{x}(X) \to T_{f(x)}(Y)$.

The chain rule remains valid as before.

\begin{prop}
	Let $X$ be a $k$-dimensional manifold with boundary. \newline
	$\Int(X)$ is a $k$-dimensional manifold (without boundary). \newline
	$\partial X$ is a $(k - 1)$-dimensional manifold (without boundary).
\end{prop}

All definitions from earlier formulated in terms of derivatives of mappings make sense verbatim when the manifolds have boundaries (immersions, submersions, regular values, transversality).

\begin{ex}
	Consider the smooth map $f : \mathbb{H}^{2} \to \mathbb{R}$ given by $(x_{1}, x_{2}) \mapsto x_{2}$. Note that $\mathbb{H}^{2}$ is a manifold with boundary. \newline
	Let $Z = \{0\}$. Then, we have $f \trans Z$, i.e., $0$ is a regular value of $f$. Indeed, let $x \in f^{-1}(Z)$. We have $\im(df_{x}) = \spn\left\{\begin{bmatrix}
		0 & 1
	\end{bmatrix}\right\}$.

	We have $f^{-1}(Z) = \partial \mathbb{H}^{2}$ -- this is a one dimensional manifold without boundary. Note that the equation
	\begin{equation*} 
		\partial(f^{-1}(Z)) = f^{-1}(Z) \cap \partial X
	\end{equation*}
	does not hold.
\end{ex}

\begin{obs}
	If $x \in \partial X$, then $T_{x}(\partial X)$ is a linear subspace of $T_{x}(X)$ of codimension $1$. \newline
	Given a map $f : X \to Y$, let $\partial f : \partial X \to Y$ denote the restriction of $f$ to $\partial X$. \newline
	The derivative of $\partial f$ at $x$ is just the restriction of $df_{x}$ to the subspace $T_{x}(\partial X)$.
\end{obs}

\begin{thm}
	Let $f$ be a smooth map of a manifold with boundary $X$ into a boundaryless manifold $Y$, and suppose that both $f : X \to Y$ and $\partial f : \partial X \to Y$ are transversal with respect to a boundaryless manifold $Z \subset Y$. Then, the preimage $f^{-1}(Z)$ is a manifold with boundary
	\begin{equation*} 
		\partial(f^{-1}(Z)) = f^{-1}(Z) \cap \partial X,
	\end{equation*}
	and $\codim_{X}(f^{-1}(Z)) = \codim_{Y}(Z)$.
\end{thm}

\begin{cor}
	Suppose that $S$ is a manifold without boundary and that $\pi : S \to \mathbb{R}$ is a smooth function with regular value $0$. Then the subset $\{s \in S : \pi(s) \ge 0\}$ is a manifold with boundary, and the boundary is $\pi^{-1}(0)$.
\end{cor}
As an application of the above corollary, we see that the closed unit ball in $\mathbb{R}^{n}$ is a manifold with boundary.

\begin{thm}[Sard's Theorem] \label{thm:sard-boundary}
	Let $f : X \to Y$ be a smooth map, where $X$ is a boundary with manifold and $Y$ is boundaryless. Almost every point of $Y$ is a regular value for both $f$ and $\partial f$.
\end{thm}

\subsection{One-Manifolds and Some Consequences}

\begin{thm}
	Every compact, connected, one-dimensional manifold with boundary is diffeomorphic to either $[0, 1]$ or $S^{1}$.
\end{thm}

\begin{cor}
	The boundary of any compact one-dimensional manifold with boundary consists of an even number of points.
\end{cor}

\begin{thm}
	If $X$ is any compact manifold with boundary, then there exists no smooth map $g : X \to \partial X$ such that $\partial g : \partial X \to \partial X$ is the identity.
\end{thm}

\begin{thm}[Brouwer Fixed-Point Theorem]
	Any smooth map $f$ of the closed unit ball into itself has a fixed point.
\end{thm}

\subsection{Transversality}

Earlier we saw that transversality is a stable property (\mynameref{thm:stability}), when the domain is compact. We now see something more valuable.

\begin{rem}
	One may generalise the idea of homotopies slightly by considering the parameter to come from a more general set than just $I$.

	Suppose $f_{s} : X \to Y$ is a family of smooth maps, indexed by a parameter $s$ that ranges over some set $S$. As we did with homotopies, consider the map $F : X \times S \to Y$ defined by $(x, s) \mapsto f_{s}(x)$. We require that the family vary smoothly by assuming $S$ to be a manifold and $F$ to be smooth.
\end{rem}

\begin{thm}[The Transversality Theorem]
	Suppose that $F : X \times S \to Y$ is a smooth map of manifolds, where only $X$ has boundary, and let $Z \subset Y$ be a boundaryless submanifold. If both $F$ and $\partial F$ are transversal to $Z$, then for almost every $s \in S$, both $f_{s}$ and $\partial f_{s}$ are transversal to $Z$.
\end{thm}
\begin{rem}
	Let $W \subset X \times S$ be the preimage of $Z$. (By the earlier results, $W$ is a manifold with boundary $\partial W = W \cap \partial(X \times S)$.) Let $\pi : W \to S$ be the projection $(x, s) \mapsto s$.

	The proof shows that if $s$ is a regular value for $\pi$, then we have $f_{s} \trans Z$ and that if $s$ is a regular value for $\partial \pi$, then we have $\partial f_{s} \trans Z$. By \mynameref{thm:sard-boundary}, the result then follows.
\end{rem}

As a consequence, we have the following: Let $f : X \to \mathbb{R}^{M}$ be a smooth map, take $S$ to be any open ball of $\mathbb{R}^{M}$, and define $F : X \times S \to \mathbb{R}^{M}$ by $F(x, s) = f(x) + s$. Fixing $x$, the map $F(x, -)$ is a submersion of $S$. In turn, $F$ is a submersion and hence, transversal to any manifold $Z \subset \mathbb{R}^{M}$. The same is true for $\partial F$ as well. (Note that $\partial(X \times S) = (\partial X) \times S$.) Fix a manifold $Z \subset \mathbb{R}^{M}$. \newline
By the transversality theorem, we have that $x \mapsto f(x) + s$ is transversal to $Z$ for almost every $s$. Thus, $f$ may be deformed into a transversal map by the addition of an arbitrarily small quantity $s$.

Some extra work needs to be done to replace the target $\mathbb{R}^{M}$ with an arbitrary manifold $Y$.	

\begin{thm}[$\epsilon$-neighbourhood Theorem]
	For a compact boundaryless manifold $Y \subset \mathbb{R}^{M}$ and a positive number $\epsilon$, let $Y^{\epsilon}$ be the open set of points in $\mathbb{R}^{M}$ with distance less than $\epsilon$ from $Y$. If $\epsilon$ is sufficiently small, then each point $w \in Y^{\epsilon}$ possesses a unique closest point in $Y$, denoted $\pi(w)$. Moreover, the map $\pi : Y^{\epsilon} \to Y$ is a submersion.

	When $Y$ is not compact, there still exists a submersion $\pi : Y^{\epsilon} \to Y$ that is the identity on $Y$, but now $\epsilon$ must be allowed to be a smooth positive function on $Y$, and $Y^{\epsilon}$ is defined as $\{w \in \mathbb{R}^{M} : \|w - y\| < \epsilon(y) \text{ for some } y \in Y\}$.
\end{thm}

\begin{cor}
	Let $f : X \to Y$ be a smooth map with $Y$ boundaryless. Then, there is an open ball $S$ in the ambient space of $Y$ and a smooth map $F : X \times S \to Y$ such that $F(-, 0) = f$, and for any fixed $x \in X$, the map $s \mapsto F(x, s)$ is a submersion $S \to Y$. In particular, both $F$ and $\partial F$ are submersions.
\end{cor}

\begin{thm}[Transversality Homotopy Theorem]
	Let $X, Y, Z$ be manifolds with $Z \subset Y$ and only $X$ having boundary. 

	For any smooth map $f : X \to Y$, there exists a smooth map $g : X \to Y$ homotopic to $f$ such that $g \trans Z$ and $\partial g \trans Z$.
\end{thm}

\begin{defn}
	Let $Y \subset \mathbb{R}^{M}$ be a manifold. For $y \in Y$, the \deff{normal space of $Y$ at $y$}, denoted $N_{y}(Y)$, is defined to be the orthogonal complement of $T_{y}(Y)$ in $\mathbb{R}^{M}$. The \deff{normal bundle of $Y$}, denoted $N(Y)$, is defined as
	\begin{equation*} 
		\{(y, v) \in Y \times \mathbb{R}^{M} : v \in N_{y}(Y)\} \subset R^{2M}.
	\end{equation*}
\end{defn}

Note that $N(Y)$ depends on the ambient space $\mathbb{R}^{M}$. There is a natural projection $\sigma : N(Y) \to Y$ defined by $(y, v) \mapsto y$.

\begin{prop}
	If $Y \subset \mathbb{R}^{M}$, then $N(Y)$ is a manifold of dimension $M$ and the projection $N(Y) \to Y$ is a submersion.
\end{prop}

\begin{defn}
	Let $C \subset X$ be an arbitrary subset. A map $f : X \to Y$ is \deff{transversal to $Z$ on $C$} if the transversality condition
	\begin{equation*} 
		\im(df_{x}) + T_{f(x)}(Z) = T_{f(x)}(Y)
	\end{equation*}
	holds for all $x \in C \cap f^{-1}(Z)$.

	This is denoted as ``$f \trans Z$ on $C$''.
\end{defn}

\begin{prop}
	If $U$ is an open neighbourhood of a closed set $C$ in $X$, then there exists a smooth function $\gamma : X \to [0, 1]$ that is identically equal to $1$ outside $U$ but is $0$ on a neighbourhood of $C$.
\end{prop}

\begin{thm}[Extension Theorem]
	Suppose that $Z$ is a \underline{closed} submanifold of $Y$, both boundaryless, and $C$ is a \underline{closed} subset of $X$. 

	Let $f : X \to Y$ be a smooth map with $f \trans Z$ on $C$ and $\partial f \trans Z$ on $C \cap \partial X$. \newline
	Then, there exists a smooth map $g : X \to Y$ homotopic to $f$, such that $g \trans Z$ and $\partial g \trans Z$, and on a neighbourhood of $C$, we have $g = f$.
\end{thm}
In less precise language: We have modified $f$ homotopically outside a neighbourhood of $C$ to make the transversality conditions hold on all of $X$. 

Picking $C = \partial X$ (this is always closed!) gives us the following corollary.

\begin{cor}
	If, for $f : X \to Y$, the boundary map $\partial f : \partial X \to Y$ is transversal to a closed submanifold $Z \subset Y$, then there exists a map $g : X \to Y$ homotopic to $f$ such that $\partial g = \partial f$ and $g \trans Z$.
\end{cor}
A useful restatement: Supposed $h : \partial X \to Y$ is transversal to $Z$. If $h$ extends to a map $X \to Y$, then $h$ extends to a map that is transversal to $Z$.

\section{Oriented Intersection Theory}

\subsection{Orientation}

Let $V$ be a vector space, and $\beta = (v_{1}, \ldots, v_{k})$ and $\beta' = (v_{1}', \ldots, v_{k}')$ be two ordered bases of $V$. Let $A : V \to V$ be the unique linear isomorphism such that $Av_{i} = v_{i}'$ for all $i \in [k]$.

\begin{defn}
	$\beta$ and $\beta'$ are said to be \deff{equivalently oriented} if $\det(A) > 0$.
\end{defn}

The above defines an equivalence relation on the set of all ordered bases of $V$. There are precisely two equivalence classes.

\begin{defn}
	An \deff{orientation of $V$} is an arbitrary decision to affix a positive sign to the elements of one equivalence class and a negative sign to the others.

	The sign given an ordered basis $\beta$ is called its \deff{orientation}, so $\beta$ is either \deff{positively oriented} or \deff{negatively oriented}, depending on which equivalence class it belongs to. 
\end{defn}

There are precisely two possible orientations for any (nonzero finite-dimensional) vector space $V$. In order to fix an orientation, it suffices to pick a standard ordered basis and assign a sign to it.

The \deff{standard orientation of Euclidean space} is the one for which the standard ordered basis is positively oriented.

For the zero vector space, an orientation is simply a choice of $+1$ or $-1$ (associated to the empty basis, if you wish).

% \textbf{Notation:} Given an ordered subset $\beta = (v_{1}, \ldots, v_{k})$ of $V$ and a map $A : V \to W$, we denote by $A\beta$ the ordered subset $(Av_{1}, \ldots, Av_{k}) \subset W$.

\begin{defn}
	Let $V$ and $W$ be oriented vector spaces, and $A : V \to W$ be a linear isomorphism. $A$ is said to \deff{preserve orientation} if $A \beta$ is a positively oriented basis of $W$ for any choice of positively oriented basis $\beta \subset V$.
\end{defn}
Note: If $\beta$ and $\beta'$ are ordered bases of $V$ from the same orientation class, then $A \beta$ and $A \beta'$ will also have the same orientation class in $W$. Thus, the above definition can be verified by checking the effect on $A$ on some fixed basis $\beta$.

\section{Integration on Manifolds}

\subsection{Exterior algebra}

We quickly recall some linear algebra. Throughout, $V$ will denote a $k$-dimensional vector space over $\mathbb{R}$ and $p$ is a positive integer.

\begin{enumerate}[leftmargin=*]
	% \item $V^{p} = \underbrace{V \times \cdots \times V}_{p \text{ times}}$.
	\item A \deff{$p$-tensor on $V$} is a multilinear function $V^{p} \to \mathbb{R}$.
	%
	\item The collection of all $p$-tensors is a vector space, denoted $\T^{p}(V^{\ast})$. \newline
	Note that $\T^{1}(V^{\ast})$ is simply the dual of $V$, denoted $V^{\ast}$.
	%
	\item If $T$ is a $p$-tensor and $S$ a $q$-tensor, then the \deff{tensor product of $T$ with $S$}, denoted $T \otimes S$, is the $(p + q)$-tensor defined by
	\begin{equation*} 
		(T \otimes S)(v_{1}, \ldots, v_{p}, v_{p + 1}, \ldots, v_{p + q}) \vcentcolon= T(v_{1}, \ldots, v_{p}) \cdot S(v_{p + 1}, \ldots, v_{p + q}).
	\end{equation*}
	%
	\item Tensor product is associative and distributes over addition. However, it is not commutative in general.
	%
	\item If $\{\phi_{1}, \ldots, \phi_{k}\}$ is a basis for $V^{\ast}$, then $\{\phi_{i_{1}} \otimes \cdots \otimes \phi_{i_{p}} : 1 \le i_{1}, \ldots, i_{p} \le k\}$ is a basis for $\T^{p}(V^{\ast})$. Consequently, $\dim(\T^{p}(V^{\ast})) = (\dim(V))^{p}$.
	%
	\item For $\sigma \in S_{p}$, we denote the sign of $\sigma$ by $(-1)^{\sigma}$. \newline
	For a $p$-tensor $T$, define $T^{\sigma}$ to be the tensor given by
	\begin{equation*} 
		T^{\sigma}(v_{1}, \ldots, v_{p}) \vcentcolon= T(v_{\sigma(1)}, \ldots, v_{\sigma(p)}).
	\end{equation*}
	If $\tau \in S_{p}$ is any permutation, one has $(T^{\sigma})^{\tau} = T^{\tau \circ \sigma}$.
	%
	\item A $p$-tensor $T$ is said to be \deff{alternating} if $T^{\pi} = (-1)^{\pi} T$ for all transpositions $\pi \in S_{p}$ (and consequently, for \emph{all} $\pi \in S_{p}$).
	%
	\item If $T$ is any $p$-tensor, we define
	\begin{equation*} 
		\Alt(T) \vcentcolon= \frac{1}{p!} \sum_{\sigma \in S_{p}} (-1)^{\sigma} T^{\sigma}.
	\end{equation*}
	Then, $\Alt(T)$ is an alternating tensor. If $T$ were alternating to begin with, then $\Alt(T) = T$.
	%
	\item The alternating $p$-tensors form a vector subspace of $\T^{p}(V^{\ast})$, denoted $\Lambda^{p}(V^{\ast})$. 
	%
	\item If $T \in \Lambda^{p}(V^{\ast})$ and $S \in \Lambda^{q}(V^{\ast})$, we define their \deff{wedge product} $T \wedge S \in \Lambda^{p + q}(V^{\ast})$ by
	\begin{equation*} 
		T \wedge S \vcentcolon= \Alt(T \otimes S).
	\end{equation*}
	Note that the above definition would make sense even if $T$ and $S$ were not alternating. However, we reserve the use of $\wedge$ for alternating tensors.
	%
	\item If $T \in \T^{p}(V^{\ast})$ and $S \in \T^{q}(V^{\ast})$ and $\Alt(T) = 0$, then $\Alt(T \otimes S) = 0 = \Alt(S \otimes T)$. 
	%
	\item Wedge product is associative. We have
	\begin{equation*} 
		(T \wedge S) \wedge R = \Alt(T \otimes S \otimes R) = T \wedge (S \wedge R)
	\end{equation*}
	for all alternating tensors $T, S, R$. \newline
	The wedge product also distributes over addition. \newline
	The wedge product is \emph{anticommutative}: if $T \in \Lambda^{p}(V^{\ast})$ and $S \in \Lambda^{q}(V^{\ast})$, then
	\begin{equation*} 
		T \wedge S = (-1)^{pq} S \wedge T.
	\end{equation*}
	In particular, if $p$ is odd, then $T \wedge T = 0$. As a special case, we have $\phi \wedge \phi = 0$ for all $\phi \in V^{\ast}$.
	%
	\item If $\{\phi_{1}, \ldots, \phi_{k}\}$ is a basis for $V^{\ast}$, then $\{\phi_{i_{1}} \wedge \cdots \wedge \phi_{i_{p}} : 1 \le i_{1} < \cdots < i_{p} \le k\}$ is a basis for $\T^{p}(V^{\ast})$. Consequently, 
	\begin{equation*} 
		\dim(\T^{p}(V^{\ast})) = \binom{k}{p} = \frac{k!}{p! (k - p)!}.
	\end{equation*}
	(Here $k = \dim(V)$.)
	%
	\item We define $\Lambda^{0}(V^{\ast}) = \mathbb{R}$. The wedge product is extended by defining the product with an element $\lambda \in \mathbb{R}$ as scalar multiplication. The wedge product then makes the direct sum
	\begin{equation*} 
		\Lambda(V^{\ast}) = \Lambda^{0}(V^{\ast}) \oplus \Lambda^{1}(V^{\ast}) \oplus \cdots \oplus \Lambda^{k}(V^{\ast})
	\end{equation*}
	a noncommutative algebra, called the \deff{exterior algebra of $V^{\ast}$}.
	%
	\item Suppose $A : V \to W$ is a linear map. Then, the transpose map $T^{\ast} : W^{\ast} \to V^{\ast}$ extends to the exterior algebras, $A^{\ast} : \Lambda^{p}(W^{\ast}) \to \Lambda^{p}(V^{\ast})$ for all $p \ge 1$ by
	\begin{equation*} 
		(A^{\ast}T)(v_{1}, \ldots, v_{p}) \vcentcolon= T(Av_{1}, \ldots, Av_{p})
	\end{equation*}
	for $T \in \Lambda^{p}(W^{\ast})$ and $(v_{1}, \ldots, v_{p}) \in V^{p}$. For $p = 0$, we define $A^{\ast}(\lambda) = \lambda$.

	Then, $A^{\ast}$ is linear, $A^{\ast}(T \wedge S) = (A^{\ast} T) \wedge (A^{\ast} S)$, and $A^{\ast}(1) = 1$. Thus, $A^{\ast}$ is an algebra homomorphism. \newline
	If $B : V \to W$ is another linear map, then $(AB)^{\ast} = B^{\ast} A^\ast$.
\end{enumerate}

\begin{thm}[Determinant Theorem] \label{thm:determinant-theorem}
	Let $V$ be a $k$-dimensional vector space.

	If $A : V \to V$ is a linear isomorphism, then $A^{\ast} : \Lambda^{k}(V^{\ast}) \to \Lambda^{k}(V^{\ast})$ is given by multiplication by the scalar $\det(A)$. 

	In particular, if $\phi_{1}, \ldots, \phi_{k} \in \Lambda^{1}(V^{\ast})$, then
	\begin{equation*} 
		A^{\ast} \phi_{1} \wedge \cdots \wedge A^{\ast} \phi_{k} = (\det(A)) \phi_{1} \wedge \cdots \wedge \phi_{k}.
	\end{equation*}
\end{thm}

\begin{defn}
	Let $V$ be an oriented $k$-dimensional vector subspace of $\mathbb{R}^{N}$. There is a unique alternating $k$-tensor $T \in \Lambda^{k}(V^{\ast})$ such that $T(v_{1}, \ldots, v_{k}) = 1/k!$ for all positively oriented ordered orthonormal bases $(v_{1}, \ldots, v_{k})$. $T$ is called the \deff{volume element of $V$}.
\end{defn}

\begin{exe}
	Show that the volume element is given as follows: Let $\phi_{1}, \ldots, \phi_{k} \in V^{\ast}$ be the (ordered) dual basis corresponding to some positively oriented ordered orthonormal basis for $V$. Then, the volume element is $\phi_{1} \wedge \cdots \wedge \phi_{k}$.
\end{exe}
\begin{soln}
	By solving this exercise, we shall show the existence of a volume element. The uniqueness then follows since $\dim(\Lambda^{k}(V^{\ast})) = 1$.

	Let $(v_{1}, \ldots, v_{k})$ be a positively oriented ordered orthonormal basis (POOOB) for $V$ and $(\phi_{1}, \ldots, \phi_{k})$ denote the dual basis. Let $(w_{1}, \ldots, w_{k})$ be any other POOOB for $V$. Then, there exists an orthogonal linear map $A : V \to V$ such that $Av_{i} = w_{i}$ for all $i$. Furthermore, since $(w_{i})_{i}$ is also positively oriented, we have $\det(A) = 1$. Now, by the \mynameref{thm:determinant-theorem}, we have
	\begin{align*} 
		1 \cdot  &= \left[(A^{\ast} \phi_{1}) \wedge \cdots \wedge (A^{\ast} \phi_{k})\right](w_{1}, \ldots, w_{k}) \\
		&= \Alt(A^{\ast}\phi_{1} \otimes \cdots \otimes A^{\ast}\phi_{k})(w_{1}, \ldots, w_{k}) \\
		&= \frac{1}{k!} \sum_{\sigma \in S_{k}} (-1)^{\sigma} (A^{\ast}\phi_{1} \otimes \cdots \otimes A^{\ast}\phi_{k})^{\sigma}(w_{1}, \ldots, w_{k}) \\
		&= \frac{1}{k!} \sum_{\sigma \in S_{k}} (-1)^{\sigma} (A^{\ast}\phi_{1} \otimes \cdots \otimes A^{\ast}\phi_{k})(w_{\sigma(1)}, \ldots, w_{\sigma(k)}) \\
		&= \frac{1}{k!} \sum_{\sigma \in S_{k}} (-1)^{\sigma} \phi_{1}(Aw_{\sigma(1)}) \cdots \phi_{k}(Aw_{\sigma(k)}).
	\end{align*}
	The only nonzero summand is when $\sigma = \id$ for otherwise we have $\sigma(i) \neq i$ for some $i$ and consequently $\phi_{i}(Aw_{\sigma(i)}) = \phi_{i}(v_{\sigma(i)}) = 0$. Thus, we are left with
	\begin{equation*} 
		(\phi_{1} \wedge \cdots \wedge \phi_{k})(w_{1}, \ldots, w_{k}) = \frac{1}{k!}. \qedhere
	\end{equation*}
\end{soln}

\subsection{Differential forms}

\begin{defn}
	Let $X$ be a smooth manifold with or without boundary. A \deff{$p$-form on $X$} is a function $\omega$ defined on $X$ such that $\omega(x) \in \Lambda^{p}[T_{x}(X)^{\ast}]$ for all $x \in X$.
\end{defn}
Note that there is no condition on $\omega$. For example, $0$-forms on $X$ are \emph{arbitrary} real-valued functions on $X$ (need not even be continuous).

The sum of two $p$-forms is defined pointwise. Similarly, if $\omega$ is a $p$-form and $\theta$ a $q$-form, then their wedge product is defined pointwise and satisfies $\omega \wedge \theta = (-1)^{pq} \theta \wedge \omega$.

\begin{defn}
	If $\phi : X \to \mathbb{R}$ is a smooth function, then $d\phi_{x} : T_{x}(X) \to \mathbb{R}$ is a linear map at each point $x$. Thus, the assignment $x \mapsto d\phi_{x}$ defines a $1$-form $d\phi$ on $X$, called the \deff{differential of $\phi$}.
\end{defn}

\begin{ex}
	Let $x_{1}, \ldots, x_{k} : \mathbb{R}^{k} \to \mathbb{R}$ denote the projection functions. Then, for each $z \in \mathbb{R}^{k}$, we have $T_{z}(\mathbb{R}^{k}) = \mathbb{R}^{k}$ and
	\begin{equation*} 
		dx_{i}(z)(a_{1}, \ldots, a_{k}) = a_{i}.
	\end{equation*}
	Thus, at each $z \in \mathbb{R}^{k}$, the linear functionals $dx_{1}(z), \ldots, dx_{k}(z)$ just form the standard basis of $(\mathbb{R}^{k})^{\ast}$.
\end{ex}

For each strictly increasing sequence $I = (i_{1}, \ldots, i_{p})$ of integers, define
\begin{equation*} 
	dx_{I} = dx_{i_{1}} \wedge \cdots \wedge dx_{i_{p}}.
\end{equation*}
The above is a $p$-form on $\mathbb{R}^{k}$.

\begin{prop}
	Every $p$-form on an open set $U \opsub \mathbb{R}^{k}$ may be uniquely expressed as a sum $\sum f_{I} dx_{I}$, over increasing index sequences with $f_{I}$ being real-valued functions on $U$.
\end{prop}

\begin{exe} \label{exe:d-phi-summation-partials}
	Show that if $\phi$ is a smooth function on $\mathbb{R}^{k}$, then
	\begin{equation*} 
		d \phi = \sum \frac{\partial \phi}{\partial x_{i}} dx_{i}.
	\end{equation*}
\end{exe}
\begin{soln}
	Both elements written above are $p$-forms and we check that they are equal by evaluating them both at an arbitrary $z \in \mathbb{R}^{k}$.

	By definition, we have $d \phi(z) = d\phi_{z}$. Note that $d\phi_{z}$ is a function from $T_{z}(\mathbb{R}^{k})$ to $\mathbb{R}$. Moreover this function is given as follows:
	\begin{equation*} 
		d \phi(z)(y_{1}, \ldots, y_{k}) = 
		\begin{bmatrix}
			\dfrac{\partial \phi}{\partial x_{1}}(z) & \cdots & \dfrac{\partial \phi}{\partial x_{k}}(z)
		\end{bmatrix}
		\begin{bmatrix}
			y_{1} \\
			\vdots \\
			y_{k} \\
		\end{bmatrix}
		= \frac{\partial \phi}{\partial x_{1}}(z) y_{1} + \cdots + \frac{\partial \phi}{\partial x_{k}}(z) y_{k}.
	\end{equation*}
	On the other hand, we noted that
	\begin{equation*} 
		dx_{i}(y_{1}, \ldots, y_{k}) = y_{i}
	\end{equation*}
	for all $i$. Thus, we get
	\begin{equation*} 
		d \phi(z)(y_{1}, \ldots, y_{k}) = \frac{\partial \phi}{\partial x_{1}}(z) dx_{1}(y_{1}, \ldots, y_{k}) + \cdots + \frac{\partial \phi}{\partial x_{k}}(z) dx_{k}(y_{1}, \ldots, y_{k}),
	\end{equation*}
	as desired.
\end{soln}

\begin{defn}
	Let $f : X \to Y$ be a smooth map, and $\omega$ a $p$-form on $Y$. The \deff{pullback of $\omega$ by $f$}, denoted $f^{\ast} \omega$, is a $p$-form on $X$ defined by
	\begin{equation*} 
		f^{\ast} \omega(x) \vcentcolon= (df_{x})^{\ast} \omega[f(x)].
	\end{equation*}
\end{defn}
Unraveling: Let $x \in X$, and set $y \vcentcolon= f(x)$. Then, we have a linear map $df_{x} : T_{x}(X) \to T_{x}(Y)$. This induces the transpose map $(df_{x})^{\ast} : \Lambda^{p}(T_{x}(Y)) \to \Lambda^{p}(T_{x}(X))$. Since $\omega(y)$ is an element of $\Lambda^{p}(T_{x}(Y))$, the above definition gives us an element of $\Lambda^{p}(T_{x}(X))$, as desired.

\begin{ex}
	When $\omega$ is a $0$-form, i.e., a function on $Y$, then the pullback $f^{\ast} \omega$ is simply the function $\omega \circ f$.
\end{ex}

\begin{exe}
	Prove the following:
	\begin{enumerate}
		\item $f^{\ast}(\omega_{1} + \omega_{2}) = f^{\ast}\omega_{1} + f^{\ast}\omega_{2}$,
		\item $f^{\ast}(\omega \wedge \theta) = (f^{\ast}\omega) \wedge (f^{\ast}\theta)$,
		\item $(f \circ h)^{\ast} \omega = h^{\ast} f^{\ast} \omega$.
	\end{enumerate}
\end{exe}

\begin{ex}
	Let $U \opsub \mathbb{R}^{k}$ and $V \opsub \mathbb{R}^{l}$, and $f : V \to U$ be smooth. Use $x_{1}, \ldots, x_{k}$ (resp. $y_{1}, \ldots, y_{l}$) for the standard coordinates on $\mathbb{R}^{k}$ (resp. $\mathbb{R}^{l}$). \newline
	Write $f = (f_{1}, \ldots, f_{k})$. The derivative $df_{y}$ at a point $y \in V$ is represented by the matrix
	\begin{equation*} 
		\left[\frac{\partial f_{i}}{\partial y_{j}}(y)\right]_{i, j}.
	\end{equation*}
	The transpose $(df_{y})^{\ast}$ on $1$-forms is given by the transpose of the above matrix.

	Consequently, given the $1$-form $dx_{i}$ (where $1 \le i \le k$), we have
	\begin{equation*} 
		f^{\ast} dx_{i}(y) = (df_{y})^{\ast} dx_{i}(f(y)).
	\end{equation*}
	The above quantity is an element of $\Lambda^{1}(T_{y}(V)) = \Lambda^{1}(\mathbb{R}^{l})$. Given $z = (z_{1}, \ldots, z_{l}) \in \mathbb{R}^{l}$, the right hand side evaluates as
	\begin{align*} 
		(df_{y})^{\ast} dx_{i}(f(y))(z) &= dx_{i}(f(y)) (df_{y}(z)).
	\end{align*}
	Now, recall that $dx_{i}(f(y))$ is simply the functional that is dual to $x_{i}$. Thus, the above quantity is simply the $i$-th coordinate of $df_{y}(z)$ and is given as
	\begin{equation*} 
		\sum_{j = 1}^{l} \frac{\partial f_{i}}{\partial y_{j}}(y) z_{j}.
	\end{equation*}
	Note that the $z_{j}$ above can in turn be written as $dy_{j}(y)(z)$. Thus, we have shown
	\begin{equation*} 
		f^{\ast} dx_{i}(y)(z) = \sum_{j = 1}^{l} \frac{\partial f_{i}}{\partial y_{j}}(y) dy_{j}(y)(z).
	\end{equation*}
	In concise notation, we have
	\begin{equation*} 
		f^{\ast} dx_{i} = \sum_{j = 1}^{l} \frac{\partial f_{i}}{\partial y_{j}} dy_{j} = d f_{i}
	\end{equation*}
	for all $1 \le i \le k$. (The second equality above is simply \Cref{exe:d-phi-summation-partials}.)
\end{ex}

\end{document}