\assign{15-04-2019}
\begin{enumerate}[label=(\arabic*)]
	\item Given $a, b \in \mathbb{Z}, a\neq0,$ consider the set $R = \{c \in \mathbb{Z}| \exists q \in \mathbb{Z}(c = b - aq)\}.$ Show that $R\cap\mathbb{N}\neq\emptyset.$ What can you say about the least element of $R\cap\mathbb{N}?$
	\item Given $a, b \in \mathbb{Z}\setminus\{0\},$ find
	\begin{enumerate*} 
		\item $\gcd(a, 0)$
		\item $\gcd(a, 1)$
		\item $\gcd(a, a).$
	\end{enumerate*}
	If $a|b,$ what is $\gcd(a, b)?$\\
	Show that $\gcd(a, b-a) = \gcd(a, b),\;\gcd(a, a+b) = \gcd(a, b),$ and $\gcd(|a|, |b|) = gcd(a, b).$
	\item Show that the set of primes in $\mathbb{N}$ is not finite.
	\item Consider the following relations on $\mathcal{A},$ identify whether it is reflexive, symmetric, transitive, or anti-symmetric.
	\begin{enumerate}[nosep] 
		\item $\mathcal{A} = \mathbb{R},$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $a \le b.$
		\item $\mathcal{A} = \mathbb{R}^2,$ and for $a = (a_1, a_2), b = (b_1, b_2) \in \mathcal{A}, a$ is related to $b$ if $a_1 \le b_1$ and $a_2 \le b_2.$\\
		What happens if `and' is replaced by `or'?
		\item $\mathcal{A}$ is the set of subsets of a set $X,$ and for $A, B \in \mathcal{A},$ $A$ is related to $B$ if $A \subset B.$
		\item $\mathcal{A}$ is the set of human beings, and for $a, b \in \mathcal{A},$\\
		$a$ is related to $b$ if $a$ is a mother/brother/sibling of $b.$
		\item $\mathcal{A}$ is the set of students at IITB in your batch, and for $a, b \in \mathcal{A},$\\
		$a$ is related to $b$ if $a$ is in the same hostel as $b.$
		\item $\mathcal{A} = \mathbb{Z},$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $12|(b - a).$
		\item $\mathcal{A} = \mathbb{R}^2,$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $a$ has the same y-coordinate as $b.$
		\item $\mathcal{A} = \mathbb{R},$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $b - a$ is an integer.
	\end{enumerate}
	In each example, pick two unrelated points in $\mathcal{A},$ and identify all points related to each.
	\item Show that every convergent sequence of real numbers is a Cauchy sequence.
	\item Show that every Cauchy sequence of real numbers is bounded.
	\item 
	\begin{enumerate}[nosep] 
		\item Show that the series $\displaystyle\sum_{k=1}^{n}\frac{1}{k}$ is a divergent series.
		\item More generally, for $p \in \mathbb{Z},$ show that $\displaystyle\sum_{k=1}^{n}\frac{1}{k^p}$ converges if and only if $p \ge 1.$
	\end{enumerate}
	\item Show that if $\displaystyle\sum_{n=1}^{\infty}a_n$ converges, then $\displaystyle\lim_{n\to \infty}a_n = 0.$\\
	The converse need not be true, i.e., if $\displaystyle\lim_{n\to \infty}a_n = 0,$ then $\displaystyle\sum_{n=1}^{\infty}a_n$ need not converge.\\
	Give an example of this phenomenon.
	\item Write $a_n$ in terms of $n$ for the following sequences:\\
	1. $\{3, 7, 11, 15, 19, \cdots\}.$ \hfill 2. $\{2, 3, 4/2, 5/6, 6/24, 7/120, \cdots\}.$\\
	3. $\{x^{3/2}, x^{9/4}, x^{15/8}, x^{21/16}, x^{27/32}, \cdots\}.$ \hfill 4. $\{1, 3, 15, 105, 945, \cdots\}.$
	\newpage
	\item Find the limits of the following sequences if they exist:\\
	\begin{multicols}{2}
		\begin{enumerate} [label = \arabic*.]
			\item $a_n = \dfrac{\sin^2(n\pi/6)}{2^n}$.
			\item $a_n = \dfrac{\ln(3 + 2e^{n^2})}{n^2 + 1}.$\\
			\item $a_n = n^p,\;p\in\mathbb{R}.$
			\item $a_n = \dfrac{n!}{n^n}.$\\
			\item $a_n = \dfrac{\ln(n)}{n}.$
			\item $a_n = \ln(n+1) - \ln(n).$\\
			\item $a_n = \dfrac{(-5)^n}{n!}.$
			\item $a_n = \dfrac{1 + 2n + 4n^3}{2 + 3n^2}.$
		\end{enumerate}
	\end{multicols}
	\item Find the limit of the series, i.e., find $\displaystyle\sum_{n=1}^{\infty}a_n$ where\\
	\begin{enumerate*} [label = (\arabic*)]
		\item $a_n = \dfrac{1}{2^n}.$
		\item $a_n = \dfrac{1}{n(n+1)}.$
		\item $a_n = \dfrac{1}{n(\ln n)^p}$ if $p > 1.$ 
	\end{enumerate*}
	\item Do the following series $\displaystyle\sum_{n=1}^{\infty}a_n$ converge or diverge?\\
	\begin{enumerate*}[label = (\arabic*)] 
		\item $a_n = sin(n\pi/2).$
		\item $a_n = \dfrac{\ln(n)}{n}.$
		\item $a_n = \dfrac{10^n}{(n+1)4^{2n+1}}.$
	\end{enumerate*}
\end{enumerate}