\assign{15-04-2019}
\begin{enumerate}[label=(\arabic*)]
	\item For $n \in \mathbb{N},$ show that the following operations on $\mathbb{Z}/n\mathbb{Z}$ are well-defined:\\
	For all $a, b \in \mathbb{Z},\;[a] + [b] = [a+b],$ and $[a][b]=[ab].$\\
	Prove that $\mathbb{Z}/n\mathbb{Z}$ is a field under these operations if and only if $n$ is a prime.
	\item Show that $\mathcal{M}_2(\mathbb{R}),$ the set of all $2\times2$ matrices with real entries, forms a group under matrix addition, and does not form a group under matrix multiplication.
	\item Let $G$ be a group and $H \subset G$ be non-empty.\\
	Show that $H$ is a subgroup if and only if $ab^{-1} \in H$ for all $a, b \in H.$
	\item Check if $H$ is a subgroup of the given group $G.$
	\begin{enumerate}[nosep] 
		\item $G = \mathbb{Z}/12\mathbb{Z};\; H = $ (i) $\{[1], [11]\}$ \hspace{1 cm} (ii) $\{[0], [3], [6], [9]\}.$\\
		Group operation being $+$ as defined above.
		\item $G = \mathcal{M}_2(\mathbb{R});\; H = $ (i) $\left\{\left.\left(\begin{array}{c c}	a & b\\ c & d \end{array}\right) \in D \right| c = 0\right\}$ (ii) the set of invertible $2\times2$ matrices.\\
		Group operation being $+$ as defined in the standard manner.
		\item $G = S_4;\; H = $ (i) $\{\text{id}, (12), (34), (12)(34)\}.$\\
		(ii) $\{(123), (134), (143), (132), (234), (243), (124), (142), \text{id}\}.$\\
		Group operation being the standard composition of cycles.
	\end{enumerate}
	\item Show that every group of prime order is cyclic.
	\item 
	\begin{enumerate}[nosep] 
		\item Find all generators for $\mathbb{Z}/12\mathbb{Z},\; \mathbb{Z}/9\mathbb{Z}$ and $\mathbb{Z}/13\mathbb{Z}.$
		\item What can you say in general about the generators of $\mathbb{Z}/n\mathbb{Z}$ for $n \in \mathbb{N}$ and $n \ge 2.$
	\end{enumerate}
	\item Consider the following relations on $\mathcal{A},$ identify whether it is an equivalence relation, a partial order, or a total order.
	\begin{enumerate}[nosep] 
		\item $\mathcal{A}$ is the set of human beings, and for $a, b \in \mathcal{A},$\\
		$a$ is related to $b$ if $a$ is a sibling of $b.$
		\item $\mathcal{A}$ is the set of students at IITB in your batch, and for $a, b \in \mathcal{A},$\\
		$a$ is related to $b$ if $a$ is in the same hostel as $b.$
		\item $\mathcal{A} = \mathbb{R},$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $a \le b.$
		\item $\mathcal{A} = \mathbb{R}^2,$ and for $a = (a_1, a_2), b = (b_1, b_2) \in \mathcal{A}, a$ is related to $b$ if $a_1 \le b_1$ and $a_2 \le b_2.$
		\item $\mathcal{A} = \mathbb{R}^2,$ and for $a = (a_1, a_2), b = (b_1, b_2) \in \mathcal{A}, a$ is related to $b$ if $a_1 \le b_1$ or $a_2 \le b_2.$
		\item $\mathcal{A}$ is the set of subsets of a set $X,$ and for $A, B \in \mathcal{A},$ $A$ is related to $B$ if $A \subset B.$
		\item $\mathcal{A} = \mathbb{Z},$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $12|(b - a).$
		\item $\mathcal{A} = \mathbb{R}^2,$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $a$ has the same y-coordinate as $b.$
		\item $\mathcal{A} = \mathbb{R},$ and for $a, b \in \mathcal{A}, a$ is related to $b$ if $b - a$ is an integer.
	\end{enumerate}
	In each example of an equivalence relation, pick a point in $a \in \mathcal{A},$ and identify $[a].$\\
	In each example of a partial (or total) order, pick a point in $\mathcal{A},$ and identify the points related to it.\\
	In the examples in $\mathbb{R}$ or $\mathbb{R}^2,$ identify these sets on the number line, or the $xy-$plane.
\end{enumerate}

