\assign{01-04-2019}
\begin{enumerate}[label=(\arabic*)]
	\item Let $a, b, c \in \mathbb{Z}.$ Prove or disprove:
	\begin{enumerate}[nosep] 
		\item If $c|(a + b),$ then $c|a$ or $c|b.$
		\item If $c|a$ or $c|b,$ then $c|ab.$
		\item If $c|ab,$ then $c|a$ or $c|b.$
	\end{enumerate}
	\item Let $W = \mathbb{Z} \cap [-100, \infty).$ Show that every non-empty subset of $W$ has a least element.
	\item Let $a_0 = 1,$ and for $n \in \mathbb{N},$ let $a_n = \sqrt{2a_{n-1}}.$
	\begin{enumerate}[nosep] 
	 	\item Show that for each $n \in \mathbb{N}, a_{n+1} \ge a_n.$ \textsc{Hint:} Use induction on $n.$
	 	\item Show that the set $\{a_n:n\in\mathbb{N}\}$ is bounded above.
	 	\item Show that the sequence $\{a_n\}_{n\in\mathbb{N}}$ is convergent and find its limit.
	\end{enumerate} 
	\item Prove or disprove: Let $(a_n)$ and $(b_n)$ be two convergent sequences of real numbers with limits $a$ and $b$ respectively. If $a_n < b_n$ for all $n \in \mathbb{N},$ then $a < b.$
	\item Show that the sequence $(p^{1/n})$ converges to $1$ for all $p > 0.$\\
	\textsc{Hint:} First prove for $p > 1$ by finding the limit of $a_n = (p^{1/n}) - 1.$
	\item %
	\begin{enumerate}[nosep] 
		\item Let $a \in (-1, \infty)$ and $n \in \mathbb{N}.$ Show that $(1 + a)^n \ge 1 + na.$
		\item Show that the sequence $a_n = (1 + 1/n)^n$ is strictly increasing.
		\item Show that the sequence $b_n = (1 + 1/n)^{n+1}$ is strictly decreasing.
		\item Show that both $(a_n)$ and $(b_n)$ converge to the same limit which lies in $(2, 4).$
	\end{enumerate}
	\item Let $A \subset \mathbb{R}$ be bounded above and $\alpha = \lub(A).$ Show that there is a sequence $(a_n)$ \underline{in $A$}, which converges to $\alpha.$
	\item Let $(a_n)$ be a bounded sequence. Recall the definition of limit inferior and limit superior defined in class. Show that
	\[\glb(a_n) \le \liminf(a_n) \le \limsup(a_n) \le \lub(a_n).\]
	\item Let $a, b \in \mathbb{Z}, L = \{c \in \mathbb{Z}|\exists k, l \in \mathbb{Z} (c = ka + lb)\},$ and $C = \{c\in\mathbb{N}| c|a \text{ and }c|b\}.$
	\begin{enumerate}[nosep] 
		\item Identify $L$ and $C$ when $(a, b) = $
		\begin{enumerate*} [label = (\arabic*)] 
			\item $(2, 3)$
			\item $(4, 6)$
			\item $(4, 8).$
		\end{enumerate*}
		\item Show that if $c \in L,$ then for all $n \in \mathbb{Z}, nc \in L.$
		\item Show that if $c \in C$ and $d|c,$ then $d \in C.$
		\item Prove or disprove: For $a, b \in \mathbb{N}, L\cap C \neq \emptyset.$
	\end{enumerate}
\end{enumerate}