\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, amsfonts, amsthm, mathtools}
\usepackage{thmtools}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage[colorlinks=true]{hyperref}
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows.meta}
\setlength\parindent{0pt}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\numberwithin{thm}{section}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{defn}[thm]{Definition}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{ex}{Example}


\let\emptyset\varnothing
\newcommand{\rel}{\;\;\operatorname{rel}\;}
\newcommand{\id}{\operatorname{id}}

\pagestyle{plain}

% \usepackage{titlesec}
% \titleformat{\section}[block]
%   {\newpage\center\normalfont}{\S\thesection}{0.25cm}{\large}

\usepackage{titlesec}
\titleformat{\section}[block]{\newpage\sffamily\Large\filcenter\bfseries}{\S\thesection.}{0.25cm}{\Large}
\titleformat{\subsection}[block]{\large\bfseries\sffamily}{\S\S\thesubsection.}{0.2cm}{\large}


\usepackage[a4paper]{geometry}
\usepackage{lipsum}

\usepackage{cleveref}
\crefname{thm}{Theorem}{Theorems}
\crefname{lem}{Lemma}{Lemmas}
\crefname{defn}{Definition}{Definitions}
\crefname{prop}{Proposition}{Propositions}
\crefname{cor}{Corollary}{Corollaries}
\crefname{equation}{}{}

\usepackage{mdframed}
\newenvironment{blockquote}
{\begin{mdframed}[skipabove=0pt, skipbelow=0pt, innertopmargin=4pt, innerbottommargin=4pt, bottomline=false,topline=false,rightline=false, linewidth=2pt]}
{\end{mdframed}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\sffamily{\S\textbf{\nouppercase{\leftmark}}}}
\fancyhead[R]{\sffamily{\thepage}}
% \renewcommand{\headrulewidth}{0pt}

% \renewcommand{\familydefault}{\rmdefault}
\usepackage{tgtermes}

\title{Algebraic Topology}
\author{Aryaman Maithani\\\url{https://aryamanmaithani.github.io/}}
% \date{Spring Semester 2019-20}

\begin{document}
\maketitle
\input{arrow-config}
In what follows, $I$ will denote the closed interval $[0, 1] \subset \mathbb{R}.$\\
Whenever we talk about a map $f:X\to Y$ between topological spaces $X$ and $Y,$ we will always mean a \emph{continuous function} $f.$\\
A path $\sigma$ in a space $X$ is a map $\sigma: I \to X.$ If $x_0 = \sigma(0)$ and $x_1 = \sigma(1),$ we write this as
\begin{equation*} 
	x_0 \overset{\sigma}{\longrightarrow} x_1.
\end{equation*}
Moreover, $x_0$ and $x_1$ are called the \emph{end points} of $\sigma.$ In particular, $x_0$ is the initial point and $x_1$ is the terminal point.\\
All the topological spaces are assumed to be nonempty.
\section{Homotopy of Paths}
%
\subsection{The Fundamental Group}

\begin{defn}[Homotopy]
	Let $\sigma$ and $\tau$ be paths in a space $X$ with the same end points, i.e., $\sigma(0) = \tau(0)$ and $\sigma(1) = \tau(1).$\\
	We say that $\sigma$ and $\tau$ are \emph{homotopic with ends points held fixed} written
	\begin{equation*} 
		\sigma \simeq \tau \rel \{0, 1\}
	\end{equation*}
	if there is a map $F: I \times I \to X$ such that
	\begin{enumerate}
		\item $F(s, 0) = \sigma(s)$ for all $s \in I,$
		\item $F(s, 1) = \tau(s)$ for all $s \in I,$
		\item $F(0, t) = x_0$ for all $t \in I,$
		\item $F(1, t) = x_1$ for all $t \in I.$
	\end{enumerate}
	$F$ is called a \emph{homotopy} from $\sigma$ to $\tau.$ We write
	\begin{equation*} 
		F : \sigma \simeq \tau \rel \{0, 1\}.
	\end{equation*}
\end{defn}
The above can be pictorially depicted as

\begin{center}
	\begin{tikzpicture}
		\def \len{2.5}
		\draw[thick, ->-=at 0.5 with label {$x_0$}](0, 0) -- (0, \len);
		\draw[thick, ->-=at 0.5 with label {$\tau$}](0, \len) -- (\len, \len);
		\draw[thick, -<-=at 0.5 with label {$x_1$}](\len, \len) -- (\len, 0);
		\draw[thick, -<-=at 0.5 with label {$\sigma$}](\len, 0) -- (0, 0);
	\end{tikzpicture}
\end{center}

The above picture is interpreted as follows: \\
Along the (bottom) line $t = 0,$ $F$ agrees with $\sigma$ and along the (top) line $t = 1,$ $F$ agrees with $t = 1.$\\
Similarly, along the (left) line $s = 0,$ $F$ is identically equal to $x_0$ and along the (right) line $s = 1,$ it is $x_1.$\\~\\
%
In particular, if $\sigma$ is a \emph{loop}, i.e., $x_0 = x_1$ and $e_{x_0}$ is the constant loop $s \mapsto x_0$ for $s \in I,$ and if $\sigma \simeq e_{x_0} \rel \{0, 1\},$ we say that ``$\sigma$ can be shrunk to a point,'' or is \emph{homotopically trivial}.

\begin{prop}[$\simeq$ is an equivalence relation] \label{prop:equivrel}
	\phantom{hi}\\
	\begin{enumerate}
		\item $\sigma \simeq \sigma \rel \{0, 1\},$
		\item $\sigma \simeq \tau \rel \{0, 1\} \implies \tau \simeq \sigma \rel \{0, 1\},$
		\item $\sigma \simeq \tau \rel \{0, 1\}$ and $\tau \simeq \rho \rel \{0, 1\} \implies \sigma \simeq \rho \rel \{0, 1\}.$ 
	\end{enumerate}
\end{prop}
\begin{proof} 
	\begin{enumerate}
		\item Define $F(s, t) \vcentcolon= \sigma(s).$
		\item Define $F(s, t) \vcentcolon= F(s, 1 - t).$
		\item Given $F:\sigma \simeq \tau \rel \{0, 1\}$ and $G:\tau \simeq \rho \rel \{0, 1\},$ define $H:I \times I \to X$ as

		\begin{equation*} 
			H(s, t) \vcentcolon= \begin{cases}
				F(s, 2t) & 0 \le 2t \le 1,\\
				G(s, 2t - 1) & 1 \le 2t \le 2.
			\end{cases}
		\end{equation*}
		Note that $F$ and $G$ do agree for $2t = 1$ since we have $F(s, 1) = \tau(s) = G(s, 0)$ for all $s \in I.$ It is easy to see that $H$ is well-defined.\\
		Note that $H$ is continuous (by the pasting lemma) and it satisfies all the four properties of a homotopy (from $\sigma$ to $\rho$), since $F$ and $G$ do so. \qedhere
	\end{enumerate}
\end{proof}
Thus, we can consider the homotopy classes $[\sigma]$ of paths $\sigma$ from $x_0$ to $x_1$ under the equivalence relation $\simeq.$ (Note very carefully that all paths in an equivalence class have the same end points.)

\begin{defn}[Multiplication of paths]
	Let $\sigma$ be a path from $x_0$ to $x_1$ and $\tau$ from $x_1$ to $x_2.$\\
	The product $\sigma*\tau$ is a path from $x_0$ to $x_2$ defined as
	\begin{equation*} 
		\sigma*\tau(s) \vcentcolon= \begin{cases}
			\sigma(2s) & 0 \le 2s \le 1,\\
			\tau(2s - 1) & 1 \le 2s \le 2.
		\end{cases}
	\end{equation*}
	Once again, it's an easy check that $\sigma\tau$ is well-defined and continuous (using the pasting lemma).
\end{defn}

The above $\sigma*\tau$ is essentially the path from $x_0$ to $x_1$ obtained by first travelling from $x_0$ to $x_1$ via $\sigma$ and then from $x_1$ to $x_2$ via $\tau.$\\~\\
We will now be lenient with notation and simply denote $\sigma*\tau$ as $\sigma\tau$ unless necessary.\\
The next proposition shows how this product behaves with the equivalence relation.

\begin{prop}
	\begin{equation*} 
		\sigma \simeq \sigma' \rel \{0, 1\} \text{ and } \tau \simeq \tau' \rel \{0, 1\} \implies \sigma\tau \simeq \sigma'\tau' \rel \{0, 1\}.
	\end{equation*}
\end{prop}
\begin{proof} 
	The proof is motivated by the following diagram.\\
	\begin{center}
		\begin{tikzpicture}
			\def \len{3}
			\draw[thick, ->-=at 0.5 with label {$x_0$}](0, 0) -- (0, \len);
			\draw[thick, ->-=at 0.5 with label {$\sigma'$}](0, \len) -- (\len, \len);
			\draw[dashed, -<-=at 0.5 with label {$x_1$}, -*-=at 0.0 with label {}, -*-=at 1.0 with label {}](\len, \len) -- (\len, 0);
			\draw[thick, -<-=at 0.5 with label {$\sigma$}](\len, 0) -- (0, 0);
			\draw[thick, ->-=at 0.5 with label {$\tau'$}](\len, \len) -- (2*\len, \len);
			\draw[thick, -<-=at 0.5 with label {$x_2$}](2*\len, \len) -- (2*\len, 0);
			\draw[thick, -<-=at 0.5 with label {$\tau$}](2*\len, 0) -- (\len, 0);
			\node[] at (\len/2, \len/2) {$F$};
			\node[] at (3*\len/2, \len/2) {$G$};
		\end{tikzpicture}
	\end{center}

	Given $F:\sigma \simeq \sigma' \rel \{0, 1\}$ and $G:\tau \simeq \tau' \rel \{0, 1\},$ define $H:I \times I \to X$ as

	\begin{equation*} 
		H(s, t)\vcentcolon= \begin{cases}
				F(2s, t) & 0 \le 2s \le 1,\\
				G(2s - 1, t) & 1 \le 2s \le 2.
			\end{cases}
	\end{equation*}

	As earlier, $H$ is well-defined (since $F(1, t) = x_1 = G(0, t)$ for all $t \in I$) and continuous. Moreover, we have
	\begin{equation*} 
		H(0, t) = F(0, t) = x_0, \quad H(1, t) = G(1, t) = x_2,
	\end{equation*}
	\begin{equation*} 
		H(s, 0)= \begin{cases}
				F(2s, 0) & 0 \le 2s \le 1,\\
				G(2s - 1, 0) & 1 \le 2s \le 2
			\end{cases} = \begin{cases}
				\sigma(2s) & 0 \le 2s \le 1,\\
				\tau(2s - 1) & 1 \le 2s \le 2
			\end{cases} = \sigma\tau(s),
	\end{equation*}
	and similarly, 
	\begin{equation*} 
		H(s, 1) = \sigma'\tau'(s)\text{ for all }s \in I.
	\end{equation*}\\
	This shows that 
	\begin{equation*} 
		H : \sigma\tau\simeq\sigma'\tau' \rel \{0, 1\}. \qedhere
	\end{equation*}
\end{proof}
\begin{defn}[Product of equivalence classes]
	In view of the above proposition, we define
	\begin{equation*} 
		[\sigma]*[\tau] \vcentcolon= [\sigma*\tau].
	\end{equation*}
\end{defn}
The above, of course, is defined only when the terminal point of $\sigma$ (and thus, any other representative of $[\sigma]$) equals the initial point of $\tau$ (and thus, any other representative of $[\tau]$).\\
As before, we shall drop the $*$ and simply write $[\sigma][\tau].$

\begin{lem} \label{lem:prodassoc}
	Let $\sigma, \tau, \omega$ be paths such that the products $\sigma(\tau\omega)$ and $(\sigma\tau)\omega$ are defined. Then,
	\begin{equation*} 
		\sigma(\tau\omega) \simeq (\sigma\tau)\omega \rel \{0, 1\}.
	\end{equation*}
\end{lem}
\begin{proof} 
	Let $x_0, x_1, x_2, x_3$ be points such that
	\begin{equation*} 
		x_0 \overset{\sigma}{\longrightarrow} x_1 \overset{\tau}{\longrightarrow} x_2 \overset{\omega}{\longrightarrow} x_3. 
	\end{equation*}
	We define a homotopy $F$ from $\sigma(\tau\omega)$ to $(\sigma\tau)\omega.$ To motivate the definition of $F,$ we may first visualise the homotopy as follows.
	\begin{center}
		\begin{tikzpicture}
			\def\len{2}
			\def\height{3}
	\draw[thick, ->-=at 0.5 with label {$x_0$}](0, 0) -- (0, \height);
	\draw[thick, ->-=at 0.5 with label {$\sigma$}](0, \height) -- (\len, \height);
	\draw[thick, ->-=at 0.5 with label {$\tau$}](\len, \height) -- (2*\len, \height);
	\draw[thick, ->-=at 0.5 with label {$\omega$}](2*\len, \height) -- (4*\len, \height);
	\draw[thick, -<-=at 0.5 with label {$x_3$}](4*\len, \height) -- (4*\len, 0);
	\draw[thick, -<-=at 0.5 with label {$\omega$}](4*\len, 0) -- (3*\len, 0);
	\draw[thick, -<-=at 0.5 with label {$\tau$}](3*\len, 0) -- (2*\len, 0);
	\draw[thick, -<-=at 0.5 with label {$\sigma$}](2*\len, 0) -- (0, 0);
	\draw[dashed,-*-=at 0.0 with label {},-*-=at 1.0 with label {}](\len, \height) -- (2*\len, 0);
	\draw[dashed, -*-=at 0.0 with label {}, -*-=at 1.0 with label {}](2*\len, \height) -- (3*\len, 0);
		\end{tikzpicture}
	\end{center}
	One can note that the top line depicts the path $(\sigma\tau)\omega$ and the bottom $\sigma(\tau\omega).$\\~\\
	We define $F:I \times I \to X$ piece-wise on the three regions (from left to right) as follows:

	\begin{equation*} 
		F(s, t) \vcentcolon= \begin{cases}
			\sigma\left(\dfrac{4s}{2 - t}\right) & 0 \le s \le \dfrac{1}{4}(2 - t) ,\\~\\
			\tau\left(4s + 2 - t\right) & \dfrac{1}{4}(2 - t) \le s \le \dfrac{1}{4}(3 - t),\\~\\
			\omega\left(\dfrac{4s + t - 3}{t + 1}\right) & \dfrac{1}{4}(3 - t) \le s \le 1.
		\end{cases}
	\end{equation*}
	It is clear that $F$ is continuous on each piece. By the pasting lemma, it is continuous everywhere.\\
	The four properties of being a homotopy are also clear, by construction. (The diagram makes it clear why.)
\end{proof}

\begin{defn}[Inverse path]
	Given a path $\sigma$ from $x_0$ to $x_1,$ its \emph{inverse path} $\sigma^{-1}$ is a path from $x_1$ to $x_0$ given by
	\begin{equation*} 
		\sigma^{-1}(s) \vcentcolon= \sigma(1 - s), \qquad s \in I.
	\end{equation*}
\end{defn}
The above is simply ``travelling backwards $\sigma$.''
\begin{lem} 
	Let $\sigma, \sigma':I \to X$ be paths such that $\sigma \simeq \sigma' \rel \{0, 1\}.$ Then,
	\begin{equation*} 
		\sigma^{-1} \simeq \sigma'^{-1} \rel \{0, 1\}.
	\end{equation*}
\end{lem}
\begin{proof} 
	Let $F:\sigma \simeq \sigma' \rel \{0, 1\}$ be a homotopy. Then, $F'(s, t) \vcentcolon= F(1 - s, t)$ is a homotopy between the inverses.
\end{proof}

\begin{defn}[Inverse class]
	Let $\sigma:I \to X$ be a path. We define the inverse of the class $[\sigma]$ as
	\begin{equation*} 
		[\sigma]^{-1} \vcentcolon= [\sigma^{-1}].
	\end{equation*}
\end{defn}
In view of the above lemma, the above definition is indeed well-defined.

\begin{lem} \label{lem:prodinv}
	Given any path $\sigma$ from $x_0$ to $x_1,$ we have
	\begin{equation*} 
		e_{x_0} \simeq \sigma\sigma^{-1} \rel \{0, 1\},
	\end{equation*}
	where $e_{x_0}$ denotes the constant loop at $x_0.$
\end{lem}

\begin{proof} 
	As usual, we motivate the proof with a diagram. In this case, it is the following:
	\begin{center}
		\begin{tikzpicture}
			\def\len{3}
			\draw[thick, ->-=at 0.5 with label {$x_0$}](0, 0) -- (0, \len);
			\draw[thick, ->-=at 0.5 with label {$\sigma$}](0, \len) -- (\len, \len);
			\draw[thick, -<-=at 0.5 with label {$e_{x_0}$}](2*\len, 0) -- (0, 0);
			\draw[thick, ->-=at 0.5 with label {$\sigma^{-1}$}](\len, \len) -- (2*\len, \len);
			\draw[thick, -<-=at 0.5 with label {$x_0$}](2*\len, \len) -- (2*\len, 0);
			\draw[dashed, -*-=at 0.5 with label {$x_1$}] (0, 0) -- (\len, \len) -- (2*\len, 0);
		\end{tikzpicture}
	\end{center}
	The homotopy $F:I \times I \to X$ in this case, is defined as
	\begin{equation*} 
		F(s, t) \vcentcolon= \begin{cases}
			\sigma(2s) & 0 \le 2s \le t,\\
			\sigma(t) & t \le 2s \le 2 - t,\\
			\sigma^{-1}(2s - 1) & 2 - t \le 2s \le 2.
		\end{cases}
	\end{equation*}
	It is clear that the piecewise definitions agree on the dashed line $2s = t.$ Observe that $\sigma^{-1}(2s - 1) = \sigma(2 - 2s)$ and thus, the functions do agree on the dashed line $2s = 2 - t$ as well. \\
	One can easily check that the four properties of the homotopy are satisfied. To see the bottom line property, note that $F(s, 0) = \sigma(0)$ (using the second piece definition) and $\sigma(0) = x_0 = e_{x_0}(s)$ for all $s \in I.$
\end{proof}

Note that since $(\sigma^{-1})^{-1} = \sigma,$ the above also shows that $\sigma^{-1}\sigma = e_{x_1}.$

\begin{lem} \label{lem:leftid}
	Let $x_0 \overset{\sigma}{\longrightarrow} x_1$ and $e_{x_0}$ be the constant path at $x_0.$ Then,
	\begin{equation*} 
		\sigma \simeq e_{x_0}\sigma \rel \{0, 1\}.
	\end{equation*}
\end{lem}
\begin{proof} 
	The proof is motivated by this diagram.

	\begin{center}
		\begin{tikzpicture}
			\def\len{3}
			\draw[thick, ->-=at 0.5 with label {$x_0$}](0, 0) -- (0, \len);
			\draw[thick, ->-=at 0.5 with label {$e_{x_0}$}](0, \len) -- (\len, \len);
			\draw[thick, -<-=at 0.5 with label {$\sigma$}](2*\len, 0) -- (0, 0);
			\draw[thick, ->-=at 0.5 with label {$\sigma$}](\len, \len) -- (2*\len, \len);
			\draw[thick, -<-=at 0.5 with label {$x_1$}](2*\len, \len) -- (2*\len, 0);
			\draw[dashed, -*-=at 1.0 with label {$x_0$}] (0, 0) -- (\len, \len);
		\end{tikzpicture}
	\end{center}

	The homotopy is $F:I\times I \to X$ defined as
	\begin{equation*} 
		F(s, t) \vcentcolon= \begin{cases}
			x_0 & 0 \le 2s \le t,\\~\\
			\sigma\left(\dfrac{2s - t}{2 - t}\right) & t \le 2s \le 2.
		\end{cases}
		\qedhere
	\end{equation*}
\end{proof}

As one would expect, we have a lemma in the other direction as well.
\begin{lem} \label{lem:rightid}
	Let $x_1 \overset{\sigma}{\longrightarrow} x_0$ and $e_{x_0}$ be the constant path at $x_0.$ Then,
	\begin{equation*} 
		\sigma \simeq \sigma e_{x_0} \rel \{0, 1\}.
	\end{equation*}
\end{lem}

\begin{proof} 
	Similar as in the last case and we omit it.
\end{proof}
	
The astute reader might have sensed a group sneaking around the corner.\\
However, note that the product of equivalence classes defined above is not a binary operation unless the endpoints are the same. Due to this, we restrict ourselves to loops in the next theorem.

\begin{thm}
	Let $\pi_1(X, x_0)$ be the set of homotopy classes of loops in $X$ at $x_0.$\\
	If multiplication in $\pi_1(X, x_0)$ is defined as above, $\pi_1(X, x_0)$ becomes a group, in which the neutral element is the class $[e_{x_0}]$ and the inverse of a class $[\sigma]$ is the class of the inverse $[\sigma^{-1}].$
\end{thm}
\begin{proof} 
	Interpreting \crefrange{lem:prodassoc}{lem:rightid} as equalities of the equivalence classes shows that $\pi_1(X, x_0)$ verifies the group axioms.
\end{proof}

The next proposition tells us how $\pi_1(X, x_0)$ and $\pi_1(X, x_1)$ are related in the case that $x_0$ and $x_1$ lie in the same path-connected component. (In the case that they do not, nothing can be said.)

\begin{prop}
	Let $\alpha$ be a path from $x_0$ to $x_1.$ The mapping $\widehat{\alpha}$ defined by
	\begin{equation*} 
		[\sigma] \mapsto [\alpha^{-1}]*[\sigma]*[\alpha] = [\alpha^{-1}\sigma\alpha]
	\end{equation*}
	is an isomorphism of the group $\pi_1(X, x_0)$ onto $\pi_1(X, x_1).$
\end{prop}
Note that the above is well-defined since $*$ is well-defined.
\begin{proof} 
	We first note that if $[\sigma] \in \pi_1(X, x_0),$ then $\alpha^{-1}\sigma\alpha$ is path as follows:
	\begin{equation*} 
		x_1 \overset{\alpha^{-1}}{\longrightarrow} x_0 \overset{\sigma}{\longrightarrow} x_0 \overset{\alpha}{\longrightarrow} x_1
	\end{equation*}
	and thus, $[\alpha^{-1}\sigma\alpha]$ is indeed an element of $\pi_1(X, x_1).$\\
	Moreover, note that
	\begin{align*} 
		\widehat{\alpha}([\sigma\sigma']) &= [\alpha^{-1}\sigma\sigma'\alpha]\\
		&= [\alpha^{-1}\sigma][\sigma'\alpha]\\
		&= [\alpha^{-1}\sigma][\alpha\alpha^{-1}][\sigma'\alpha]\\
		&= [\alpha^{-1}\sigma\alpha][\alpha^{-1}\sigma'\alpha]\\
		&= \widehat{\alpha}([\sigma])\widehat{\alpha}([\sigma']).
	\end{align*}
	This shows that $\widehat{\alpha}$ is a homomorphism. That this is an isomorphism follows by noting that it has as inverse $\widehat{\alpha^{-1}}.$
\end{proof}
\begin{cor}
	If $X$ is pathwise connected, the group $\pi_1(X, x_0)$ is independent of the point $x_0,$ up to isomorphism.
\end{cor}
Note that if $C$ is a connected component of $X$ containing $x_0,$ then $\pi_1(X, x_0) = \pi_1(C, x_0)$ since any loop at $x_0$ must necessarily lie in $C.$ For this reason, we might as well only work with pathwise connected spaces.
\begin{defn}
	If $X$ is pathwise connected, we write $\pi_1(X)$ for $\pi_1(X, x_0)$ and call it \emph{the fundamental group} of $X.$
\end{defn}
Note that this group depends on $x_0$ in the sense that the elements of the group depend on the base point $x_0$ but the isomorphism class does not.\\
\begin{defn}[Simply connected]
	A space $X$ is called simply connected if it is pathwise connected and its fundamental group is trivial.
\end{defn}
\begin{lem} \label{lem:simpconnpathshomot}
	Let $X$ be simply connected. If $\sigma$ and $\tau$ are paths in $X$ with the same initial and terminal points, then $\sigma \simeq \tau \rel \{0, 1\}.$
\end{lem}
\begin{proof} 
	Let the initial and terminal points be $x_0$ and $x_1,$ respectively.\\
	Consider the path $\sigma\tau^{-1},$ which is path at $x_0.$ Since $X$ is simply connected, we have
	\begin{equation*} 
		\sigma\tau^{-1} \simeq e_{x_0} \rel \{0, 1\}.
	\end{equation*}
	By the previously seen properties, we see that
	\begin{equation*} 
		(\sigma\tau^{-1})\tau \simeq e_{x_0}\tau \rel \{0, 1\}
	\end{equation*}
	or
	\begin{equation*} 
		\sigma \simeq \tau \rel \{0, 1\}. \qedhere
	\end{equation*}
\end{proof}
\subsection{Functoriality}
We now wish to turn $\pi_1$ into a functor. Since we need to take care of the base points, we look at the category of \emph{Pointed Topological spaces}.
\begin{defn}[Pointed Topological Spaces]
	The category $\mathsf{Top}_\bullet$ of \emph{pointed topological spaces} is the category whose objects and morphisms are given as follows:
	\begin{itemize}
		\item Objects: Pairs $(X, x_0)$ where $X$ is a topological space and $x_0 \in X,$
		\item Morphisms: $f:(X, x_0) \to (Y, y_0)$ such that $f:X\to Y$ is a continuous function and $f(x_0) = y_0.$
	\end{itemize}
\end{defn}
That the above is a category can be easily verified.

\begin{defn}
	Let $h:(X, x_0) \to (Y, y_0)$ be a morphism. Define
	\begin{equation*} 
		h_* : \pi_1(X, x_0) \to \pi_1(Y, y_0)
	\end{equation*}
	by the equation
	\begin{equation*} 
		h_*([\sigma]) = [h\circ \sigma].
	\end{equation*}
	The map $h_*$ is called the \emph{homomorphism induced by $h$}, relative to the base point $x_0.$
\end{defn}
To see that $h_*$ is well-defined, we note that if 
\begin{equation*} 
	F : \sigma \simeq \sigma' \rel \{0, 1\}
\end{equation*}
for loops $\sigma, \sigma'$ in $X$ at $x_0,$ then
\begin{equation*} 
	h \circ F : h\circ \sigma \simeq h\circ\sigma' \rel \{0, 1\}.
\end{equation*}
That is to say, if two loops at $x_0$ are homotopic, then so are the loops obtained by pre-composing $h.$\\~\\
To see that $h_*$ is a homomorphism, first note that
\begin{equation*} 
	(h \circ \sigma)(h \circ \sigma') = h\circ(\sigma\sigma').
\end{equation*}
(This follows from the definition of the product of paths.)\\
Then, we see that
\begin{equation*} 
	h_*([\sigma\sigma']) = [h\circ(\sigma\sigma')] = [h\circ\sigma][h\circ\sigma'] = h_*([\sigma])h_*([\sigma']).
\end{equation*}

\begin{thm}[Functoriality]
	If $h:(X, x_0) \to (Y, y_0)$ and $k:(Y, y_0) \to (Z, z_0)$ are morphisms, then
	\begin{equation*} 
		(k \circ h)_* = k_* \circ h_*.
	\end{equation*}
	If $i:(X, x_0) \to (X, x_0)$ is the identity map, then $i_*$ is the identity homomorphism.
\end{thm}
\begin{proof} 
	By definition, we have
	\begin{align*} 
		(k \circ h)_*([\sigma]) &= [(k \circ h) \circ \sigma]\\
		&= [k \circ (h \circ \sigma)]\\
		&= k_*([h\circ \sigma])\\
		&= k_*(h_*([\sigma]))\\
		&= (k_* \circ h_*)([\sigma]).
	\end{align*}
	Thus, $(k \circ h)_* = k_* \circ h_*.$\\~\\
	Now, if $i$ is the identity map, then we have
	\begin{equation*} 
		i_*([\sigma]) = [i \circ \sigma] = [\sigma],
	\end{equation*}
	showing that $i_*$ is the identity map of $\pi_1(X, x_0).$
\end{proof}
The above then shows that $\pi_1$ defines a functor from the category $\mathsf{Top}_*$ to $\mathsf{Grp}.$\\
Since functors preserve isomorphisms in general, we get the following corollary.
\begin{cor}
	If $h:(X, x_0) \to (Y, y_0)$ is a morphism such that $h:X \to Y$ is a homeomorphism, then
	\begin{equation*} 
		h_* : \pi_1(X, x_0) \to \pi_1(Y, y_0)
	\end{equation*}
	is an isomorphism.
\end{cor}
Since we aren't discussing Category Theory, we give a proof for this special example of functors.
\begin{proof} 
	Let $h^{-1}:Y \to X$ be the inverse, which is continuous since $h$ is a homeomorphism. Moreover, $h^{-1}(y_0) = x_0$ and thus, $h^{-1}:(Y, y_0) \to (X, x_0)$ is a morphism and the inverse of $h.$\\
	Now, note that,
	\begin{equation*} 
		(h_*)\circ((h^{-1})^*) = (h\circ h^{-1})^* = (\id_{(Y, y_0)})^* = \id_{\pi_1(Y, y_0)},
	\end{equation*}
	by functoriality. Similarly, we have
	\begin{equation*} 
		((h^{-1})^*)\circ(h_*) = \id_{(X, x_0)},
	\end{equation*}
	proving the corollary.
\end{proof}
%
%
\section{Homotopy of Maps}
%
In the previous section, we talked about homotopy of special types of maps. More precisely, we only considered maps $I \to X.$ However, we can replace $I$ by an arbitrary topological space $Y.$ In the place of endpoints, we just consider a subspace $A \subset Y.$
\begin{defn}[Relative homotopy]
	Given maps $f, g:Y \to X$ such that $f|_A = g|_A,$ we say $f$ and $g$ are homotopic relative to $A$ written
	\begin{equation*} 
		f \simeq g \rel A
	\end{equation*}
	if there is a map $F:Y \times I \to X$ satisfying
	\begin{enumerate}
		\item $F(y, 0) = f(y)$ for all $y \in Y,$
		\item $F(y, 1) = g(y)$ for all $y \in Y,$
		\item $F(a, t) = f(a) = g(a)$ for all $a \in A, t \in I.$
	\end{enumerate}
	This map $F$ is called a homotopy from $f$ to $g$ relative to $A$ and we write
	\begin{equation*} 
		F:f\simeq g \rel A.
	\end{equation*}
\end{defn}
Note that the ``second coordinate'' above is still $I.$\\
Note that (3) is satisfied vacuously if $A = \emptyset$ and we have $f|_A = g|_A$ for all maps $f, g : Y \to X.$ Keeping this in mind, we have the following definition.
\begin{defn}[Homotopy]
	Maps $f, g:Y \to X$ are said to be \emph{homotopic} if $f$ and $g$ are homotopic relative to $\emptyset.$\\
	We write this more simply as
	\begin{equation*} 
		f \simeq g.
	\end{equation*}
	Moreover, any $F$ as before is simply called a homotopy from $f$ to $g.$\\
	As before, we write
	\begin{equation*} 
		F:f\simeq g.
	\end{equation*}
\end{defn}

Once again, we obtain an equivalence. The homotopies defined as in the proof of \cref{prop:equivrel} work again.
\begin{defn}[Contractible space] \label{def:contrac}
	If $X$ is a topological space such that the identity map on $X$ is homotopic to a constant map on some point in $X,$ we say that $X$ is \emph{contractible}.
\end{defn}

\begin{prop} \label{prop:contracpathwise} % ex 3.1
	$X$ is contractible if and only if for any space $Y,$ any two maps of $Y$ into $X$ are homotopic. A contractible space is pathwise connected.
\end{prop}
\begin{proof} 
	$(\implies)$ Let $X$ be contractible and $Y$ be any space. Fix any $x_0 \in X$ such that $\id_X$ is homotopic to the constant map $e_{x_0}:X\to X.$ \\
	Let $f_{x_0}:Y\to X$ denote the constant map $y \mapsto x_0.$\\
	Now, given any map $f:Y\to X,$ we show that it is homotopic to $f_{x_0}.$ \\This will prove that any two maps of $Y$ into $X$ are homotopic since $\simeq$ is an equivalence relation.\\
	Let $H:\id_X \simeq e_{x_0}$ be any homotopy. Then, we have
	\begin{equation*} 
		H(x, 0) = x,\quad H(x, 1) = x_0; \qquad \text{for all } x \in X.
	\end{equation*}
	(Note that $H$ is continuous.)\\
	Now, we define $F:Y\times I \to X$ as
	\begin{equation*} 
		F(y, t) = H(f(y), t).
	\end{equation*}
	It is clear that $F$ is a map. (That is, $F$ is continuous.)\\
	Moreover, note that
	\begin{equation*} 
		F(y, 0) = H(f(y), 0) = f(y), \quad F(y, 1) = H(f(y), 1) = x_0 = f_{x_0}(y); \qquad \text{for all } y \in Y.
	\end{equation*}
	This shows that $F:f\simeq f_{x_0},$ as desired.\\~\\
	$(\impliedby)$ To show that $X$ is contractible, simply consider $Y = X$ and consider the maps $\id_X$ and $e_{x_0}.$ (Both of these are indeed continuous.)\\
	By hypothesis, these maps are homotopic and by definition, $X$ is contractible.\\~\\
	Now, we show that $X$ is pathwise connected assuming that it is contractible.\\
	Let $x_0$ and $x_1$ be any two points in $X.$ As $X$ is contractible, $(\implies)$ tells us that the maps $e_{x_0}$ and $e_{x_1}$ are homotopic. \\
	Let $F$ be any homotopy from $e_{x_0}$ and $e_{x_1}.$ Define $\sigma:I\to X$ as 
	\begin{equation*} 
		\sigma(t) \vcentcolon= F(x_0, t).
	\end{equation*}
	$\sigma$ is clearly continuous. Moreover, we have
	\begin{align*} 
		\sigma(0) &= F(x_0, 0) = e_{x_0}(x_0) = x_0,\\
		\sigma(1) &= F(x_0, 1) = e_{x_1}(x_0) = x_1.
	\end{align*}
	Thus, $\sigma$ is path from $x_0$ to $x_1$ in $X,$ proving the proposition.
\end{proof}
\begin{ex}
	Every convex subset $X$ of Euclidean space is contractible.\\
	Given maps $f_1, f_2: Y \to X,$ we have a homotopy $F:f_1 \simeq f_2$ given by
	\begin{equation*} 
		F(y, t) = tf_2(y) + (1 - t)f_1(y), \quad y \in Y, t \in I.
	\end{equation*}
	By the convexity assumption, the above $F$ is indeed a map into $X.$\\
	By the previous proposition, this shows that $X$ is contractible.
\end{ex}
\begin{ex}
	$\mathbb{R}^n$ is contractible for any $n.$\\
	To see this, we could either appeal to the previous example or do it directly by defining a homotopy $F: e_{0} \simeq \id_{\mathbb{R}^n}$ as
	\begin{equation*} 
		F(x, t) = tx.
	\end{equation*}
\end{ex}

We would now like to show that any contractible space is simply connected. What we do know is that any loop would be homotopic to a point. However, we do not know if this homotopy is relative to $\{0, 1\}.$ Indeed, to show that we do have a homotopy relative to $\{0, 1\},$ we would need to use the fact that $X$ is contractible once again.\\
Before proving that, we first look at a lemma.

\begin{lem} \label{lem:gbad}
	Let $F:I\times I \to X$ be a map. Set $\alpha(t) = F(0, t),$ $\beta(t) = F(1, t),$ $\gamma(s) = F(s, 0),$ and $\delta(s) = F(s, 1),$ as in the diagram
	\begin{center}
		\begin{tikzpicture}
			\def \len{3}
			\draw[thick, ->-=at 0.5 with label {$\alpha$}](0, 0) -- (0, \len);
			\draw[thick, ->-=at 0.5 with label {$\delta$}](0, \len) -- (\len, \len);
			\draw[thick, -<-=at 0.5 with label {$\beta$}](\len, \len) -- (\len, 0);
			\draw[thick, -<-=at 0.5 with label {$\gamma$}](\len, 0) -- (0, 0);
			\node[] at (\len/2, \len/2) {$F$};
		\end{tikzpicture}
	\end{center}
	Then, $\delta = \alpha^{-1}\gamma\beta.$
\end{lem}
\begin{proof} 
	The proof is quite intuitive. First, we define the paths
	\begin{equation*} 
		\sigma:I \to I\times I, \quad \tau:I \to I \times I
	\end{equation*}
	as
	\begin{equation*} 
		\sigma(s) \vcentcolon= (t, 1)
	\end{equation*}
	and
	\begin{equation*} 
		\tau(s) \vcentcolon= \begin{cases}
			(0, 1 - 4s) & 0 \le 4s \le 1, \\
			(4s - 1, 0) & 1 \le 4s \le 2, \\
			(1, 2s - 1) & 1 \le 2s \le 2.
		\end{cases}
	\end{equation*}
	These paths are the following ones in $I^2:$
	\begin{center}
		\begin{tikzpicture}
			\def \len{3}
			\draw[thick, ->-=at 0.5 with label {$\sigma$}](0, \len) -- (\len, \len);
			\draw[red, thick, -<-=at 0.5 with label {}](0, 0) -- (0, \len);
			\draw[red, thick, -<-=at 0.5 with label {}](\len, \len) -- (\len, 0);
			\draw[red, thick, -<-=at 0.5 with label {$\tau$}](\len, 0) -- (0, 0);
		\end{tikzpicture}
	\end{center}
	As it should be clear from the diagram (and one can easily check), we have
	\begin{equation*} 
		\delta = F \circ \sigma, \quad (\alpha^{-1}\gamma)\beta = F \circ \tau.
	\end{equation*}
	(Note that the bracketing in $(\alpha^{-1}\gamma)\beta$ is necessary.)\\
	Also, since $I^2$ is convex, we see that $\sigma$ and $\tau$ are homotopic relative to $\{0, 1\}$ with $H:I\times I \to I\times I$ being a required homotopy defined as
	\begin{equation*} 
		H(s , t) \vcentcolon= (1 - t)\sigma(s) + t\tau(s).
	\end{equation*}
	Thus,
	\begin{align*} 
		F \circ H &: F \circ \sigma \simeq F \circ \tau \rel \{0, 1\}\\
		\implies F \circ H &: \delta \simeq (\alpha^{-1}\gamma)\beta \rel \{0, 1\},
	\end{align*}
	as desired.
\end{proof}	
\begin{thm}
	Let $X$ be a contractible space. Then, $X$ is simply connected.
\end{thm}
\begin{proof} 
	Note that by \cref{prop:contracpathwise}, we know that $X$ is pathwise connected. Now we show that that $\pi_1(X)$ is trivial.\\
	Let $x_0 \in X$ be arbitrary and $\alpha:I\to X$ be a loop at $x_0$ in $X.$\\
	If we show that $\alpha \simeq e_{x_0} \rel \{0, 1\},$ then we are done.\\~\\
	To do this, we will use the earlier lemma after constructing an appropriate $F.$\\
	Using that $X$ is contractible, we fix a homotopy $H:\id_X \simeq f_{x_0}$ where $f_{x_0}:X\to X$ is the constant function $x \mapsto x_0.$\\
	(This is different from $e_{x_0}$ since the domains are different in general.)\\
	To recall, $H$ has the following properties:
	\begin{equation*} 
		H(x, 0) = x,\; H(x, 1) = x_0 \quad \text{for all } x \in X.
	\end{equation*}
	Now, we define $F:I\times I \to X$ as 
	\begin{equation*} 
		F(s, t) \vcentcolon= H(\sigma(s), t).
	\end{equation*}
	Now, note that if we set $\alpha, \beta, \gamma, \delta$ as in the previous lemma, we have
	\begin{align*} 
		\alpha(t) = F(0, t) = H(\sigma(0), t) &= H(x_0, t)\\
		&= H(\sigma(1), t) = F(1, t) = \beta(t),
	\end{align*}
	\begin{equation*} 
		\gamma(s) = F(s, 0) = H(\sigma(s), 0) = \sigma(s),
	\end{equation*}
	\begin{equation*} 
		\delta(s) = F(s, 1) = H(\sigma(s), 1) = x_0.
	\end{equation*}
	In other words, we have
	\begin{equation*} 
		\alpha = \beta, \gamma = \sigma, \delta = e_{x_0}.
	\end{equation*}
	By the previous lemma, we know that $[\delta] = [\alpha^{-1}\gamma\beta],$ where $[.]$ is the homotopy class of a path relative to $\{0, 1\}.$ Thus, we have
	\begin{align*} 
		[e_{x_0}] &= [\alpha^{-1}\sigma\alpha]\\
		\implies [\alpha][e_{x_0}][\alpha^{-1}] &= [\sigma]\\
		\implies [e_{x_0}] &= [\sigma]\\
		\implies e_{x_0} &\simeq \sigma \rel \{0, 1\},
	\end{align*}
	finishing the proof.
\end{proof}

\begin{prop} \label{prop:homsamehomo}
	Let $f, g:Y\to X$ be maps which are homotopic by means of a homotopy $F:Y \times I \to X.$ \\
	Let $y_0 \in Y,$ $x_0 \vcentcolon= f(y_0) = F(y_0, 1),$ and $x_1 \vcentcolon= g(y_0) = F(y_0, 1).$\\
	Let $\alpha:I \to X$ be a path from $x_0$ to $x_1$ given by
	\begin{equation*} 
		\alpha(t) = F(y_0, t) \quad t \in I.
	\end{equation*}
	Then, the following diagram commutes.
	\begin{center}
		\begin{tikzcd}
			{\pi_1(Y, y_0)} \arrow[rr, "f_*"] \arrow[rrddd, "g_*"'] & & {\pi_1(X, x_0)} \arrow[ddd, "\widehat{\alpha}"] \\
			&&\\&&\\
			&& {\pi_1(X, x_1)}
		\end{tikzcd}
	\end{center}
\end{prop}

\begin{proof} 
	The diagram commuting is just saying that
	\begin{equation*} 
		\widehat{\alpha} \circ f_* = g_*.
	\end{equation*}
	Let $[\sigma] \in \pi_1(Y, y_0)$ be arbitrary. Showing that the above is true is equivalent to showing that 
	\begin{equation*} 
		(\widehat{\alpha} \circ f_*)([\sigma]) = g_*([\sigma]).
	\end{equation*}
	Using the definitions of $\widehat{\alpha}$ and $f_*,$ we note that
	\begin{align*} 
		(\widehat{\alpha} \circ f_*)([\sigma]) &= g_*([\sigma])\\
		\iff \widehat{\alpha}(f_*([\sigma])) &= g_*([\sigma])\\
		\iff \widehat{\alpha}([f\circ \sigma]) &= [g\circ \sigma]\\
		\iff [\alpha^{-1}(f\circ \sigma) \alpha] &= [g\circ \sigma].
	\end{align*}
	Now, defining $\tilde{F}:I\times I \to X$ as
	\begin{equation*} 
		\tilde{F}(s, t) = F(\sigma(s), t).
	\end{equation*}
	Then, we have the following diagram as in \cref{lem:gbad} which proves the proposition.
	\begin{center}
		\begin{tikzpicture}
			\def \len{3}
			\draw[thick, ->-=at 0.5 with label {$\alpha$}](0, 0) -- (0, \len);
			\draw[thick, ->-=at 0.5 with label {$g\circ\sigma$}](0, \len) -- (\len, \len);
			\draw[thick, -<-=at 0.5 with label {$\alpha$}](\len, \len) -- (\len, 0);
			\draw[thick, -<-=at 0.5 with label {$f\circ\sigma$}](\len, 0) -- (0, 0);
			\node[] at (\len/2, \len/2) {$\tilde{F}$};
		\end{tikzpicture}
	\end{center}
	To see that the sides are indeed as labeled, recall that $\sigma$ is a loop at $y_0$ and note that
	\begin{align*} 
		\tilde{F}(0, t) &= F(\sigma(0), t) = F(y_0, t) = \alpha(t),\\
		\tilde{F}(1, t) &= F(\sigma(1), t) = F(y_0, t) = \alpha(t),\\
		\tilde{F}(s, 0) &= F(\sigma(s), 0) = g(\sigma(s)) = (g\circ \sigma)(s),\\
		\tilde{F}(s, 1) &= F(\sigma(s), 1) = f(\sigma(s)) = (f\circ \sigma)(s).
	\end{align*}
	By the conclusion of \cref{lem:gbad}, we are done.
\end{proof}
Recall that $\widehat{\alpha}$ is an isomorphism and thus, we get the following corollary.
\begin{cor} \label{cor:homsameiso}
	With the same setup as above, $f_*$ is an isomorphism if and only if $g_*.$
\end{cor}
What the above corollary says is that if $f$ and $g$ are homotopic, then $f_*$ is an isomorphism iff $g_*$ is.

\begin{defn}[Homotopy equivalence]
	A map $f:Y \to X$ is said to be a \emph{homotopy equivalence} if there exists a map $f':X \to Y$ such that
	\begin{align*} 
		ff' & \simeq \id_X,\\
		f'f & \simeq \id_Y.
	\end{align*}
	If such a map exists, we say that $X$ and $Y$ are \emph{homotopically equivalent spaces}.
\end{defn}
It can be checked that being homotopically equivalent is an ``equivalence relation.''

\begin{cor}
	If $f:Y \to X$ is a homotopy equivalence, then $f_*$ is an isomorphism
	\begin{equation*} 
		\pi_1(Y, y_0) \to \pi_1(X, f(y_0))
	\end{equation*}	
	for any $y_0 \in Y.$
\end{cor}
\begin{proof} 
	Let $f':X \to Y$ be as in the definition.\\
	Then, $ff' \simeq \id_X.$ By the previous corollary, we have that $(ff')_*$ is an isomorphism. (Since $(\id_X)_*$ is.)\\
	Similarly, $(f'f)_*$ is an isomorphism. Since $(ff')_* = f_*\circ f'_*$ and $(f'f)_* = f'_* \circ f_*,$ we see that $f_*$ is a bijection and hence, an isomorphism.
\end{proof}

The above shows that the fundamental group of a path-connected space is a \emph{homotopy invariant}. We had shown earlier that this was a topological invariant. \\
Note that being homotopically equivalent is a weaker concept than being topologically invariant (i.e., homeomorphic). Clearly, if $f:X \to Y$ is a homeomorphism, it also a homotopy equivalence with $f' = f^{-1}.$\\
However, the closed interval $I$ is homotopically equivalent to the point space but clearly not homeomorphic. In fact, one can note that $X$ is contractible if and only if it is homeomorphic to a point.
%
%
\section{Fundamental Group of the Circle}
In this section, we prove a more general result. $S^1$ will turn out to be a special case of that. First, we need a lemma.
\begin{lem} \label{lem:unifcont}
	Let $K$ be a compact metric space and $G$ a topological group. Let $V \subset G$ be open such that $1 \in V.$\\
	If $f:K\to G$ is continuous, then there exists $\delta > 0$ such that 
	\begin{equation*} 
		d(k, k') < \delta \implies f(k)(f(k'))^{-1} \in V.
	\end{equation*}
\end{lem}
The above is essentially mimicking something like ``uniform continuity.''
\begin{proof} \phantom{hi}

	\begin{blockquote}
		\textbf{Claim 1.} There exists an open set $U \subset G$ such that
		\begin{enumerate}
			\item $1 \in U \subset V,$
			\item $g, g' \in U \implies gg^{-1} \in V.$
		\end{enumerate}
		\begin{proof} 
			The function $\varphi:G \times G \to G$ defined as
			\begin{equation*} 
				\varphi(g, g') \vcentcolon= g(g')^{-1}
			\end{equation*}
			is continuous. Thus, $\varphi^{-1}(V)$ is open.\\
			Note that $(1, 1) \in \varphi^{-1}(V).$ Thus, there exists a basis element of the form $U_1 \times U_2$ satisfying
			\begin{equation*} 
				(1, 1) \in U_1 \times U_2 \subset \varphi^{-1}(V).
			\end{equation*}
			Let $U\vcentcolon= U_1 \cap U_2 \cap V.$ Clearly, $U$ is open and $1 \in U \subset V.$ \\
			Moreover,
			\begin{align*} 
				g, g' \in U \implies (g, g') \in U_1 \times U_2 \subset \varphi^{-1}(V) \implies \varphi(g, g') \in V \implies g(g')^{-1} \in V,
			\end{align*}
			as desired.
		\end{proof}
	\end{blockquote}
		With this, we can mimic the proof of continuous functions being uniformly continuous on compact sets. (The above $U$ will help us use ``triangle inequality'' in the codomain.)\\
		Let $U$ be as in the above claim.\\
	\begin{blockquote}
		\textbf{Claim 2.} Given any $k \in K,$ there exists $\delta_k > 0$ such that
		\begin{align*} 
			d(k, k') < \delta_k &\implies f(k)(f(k'))^{-1} \in U, \\
			d(k, k') < \delta_k &\implies f(k')(f(k))^{-1} \in U.	
		\end{align*}
		\begin{proof} 
			The function $f_k : K \to G$ defined by $f_k(k') = f(k)(f(k'))^{-1}$ is continuous with $f_k(k) = 1 \in U.$\\
			Consider the open set $f_k^{-1}(U).$ Since it contains $k,$ there exists $\delta > 0$ such that $B_\delta(k) \subset f_k^{-1}(U).$ Thus, if $k' \in B_\delta(k),$ then $f_k(k') \in U,$ as desired for the first condition.\\~\\
			Note that we can find a suitable $\delta_k'$ for the other condition as well. Taking the minimum of the two proves the claim.
		\end{proof}
	\end{blockquote}
	Let $V_k = B_{\delta_k/2}(k).$ Clearly, $\{V_k\}_{k \in K}$ is an open cover of $K.$ Since $K$ is compact, we may extract a finite subcover.\\
	Let $k_1, \ldots, k_n$ be the indices of one such. Set 
	\begin{equation*} 
		\delta \vcentcolon= \min_{1 \le i \le n} \dfrac{1}{2}\delta_{k_i}.
	\end{equation*}
	Clearly, $\delta > 0.$ Moreover, it satisfies the condition of the lemma. To see this, let $k, k' \in K$ be such that $d(k, k') < \delta.$\\
	Since $\{V_{k_i}\}_{1 \le i \le n},$ is an open cover, $k$ lies in $V_{k_i}$ for some $1 \le i \le n.$ That is, $2d(k, k_i) < \delta_i.$ Now, using triangle inequality, note that
	\begin{equation*} 
		d(k', k_i) \le d(k', k) + d(k, k_i) < \delta + \frac{1}{2}\delta_i \le \dfrac{1}{2}\delta_i + \dfrac{1}{2}\delta_i = \delta_i.
	\end{equation*}
	Thus, both $k$ and $k'$ are at most $\delta_i$ from $k_i.$ By the definition of $\delta_i$ (from Claim 2), we see that $f(k)(f(k_i))^{-1} \in U$ and $f(k_i)(f(k'))^{-1} \in U.$\\
	By the property of $U,$ we have
	\begin{equation*} 
		(f(k)(f(k_i))^{-1})((k_i)(f(k'))^{-1}) = f(k)(f(k'))^{-1} \in V,
	\end{equation*}
	as desired.
\end{proof}

Now, for the remainder of this section, we shall fix $G$ as any simply connected topological group and $H \le G$ is a \emph{discrete} normal subgroup of $G.$ We will show that $\pi_1(G/H, 1) \cong H.$\\
(In the special case that $G = \mathbb{R}$ and $H = \mathbb{Z},$ we see that $\pi_1(S^1, 1) \cong \mathbb{Z}$ or simply, $\pi_1(S^1) \cong \mathbb{Z}.$)\\~\\
We also fix the map $\varphi:G \to G/H$ to be the projection $g \mapsto gH.$\\
\begin{lem} 
	There exists an open neighbourhood $U$ of $1$ in $G$ which is mapped homeomorphically onto an open neighbourhood $V$ of $1$ in $G/H$ be $\varphi.$
\end{lem}
\begin{proof} 
	Since $H$ is discrete, $\{1\}$ is open in $H.$ Thus, there exists an open neighbourhood $U_1$ of $1$ in $G$ such that $U_1 \cap H = \{1\}.$\\
	As in claim 1 of the previous proof, we may find a subset $U \subset U_1$ such that $g, g' \in U \implies gg'^{-1} \in U_1.$ Clearly, $U \cap H =\{1\}$ as well. \\
	\begin{blockquote}
		\textbf{Claim 1.} $\varphi|_U$ is injective.
	\begin{proof} 
		Let $g_1, g_2 \in U$ with $\varphi(g_1) = \varphi(g_2).$\\
		Then, $g_1H = g_2H$ or $Hg_1 = Hg_2$ or $Hg_1g_2^{-1} = H$ or $g_1g_2^{-1} \in H.$\\
		Since $g_1, g_2 \in U,$ we also have $g_1g_2^{-1} \in U_1.$ Since $U_1 \cap H = \{1\},$ we see that $g_1g_2^{-1} = 1$ or $g_1 = g_2.$
	\end{proof}
	\end{blockquote}
	Let $V = \varphi(U).$ Clearly, $\varphi$ maps $U$ bijectively onto $V$, in view of the previous claim. Moreover, this must be a homeomorphism. To see this, we recall a general result.
	\begin{blockquote}
		\textbf{Claim 2.} The quotient map $\phi:G \to G/H$ is open.
	\begin{proof} 
		Let $W$ be an open subset of $G.$ The set
		\begin{equation*} 
			WH = \{wh : w \in W, h \in H\}
		\end{equation*}
		is open since $WH = \displaystyle\bigcup_{h \in H}Wh,$ which is a union of open subsets of $G$ since right multiplication is a homeomorphism.\\
		Note that $\varphi^{-1}(\varphi(W)) = WH.$ Since $\varphi$ is a quotient map and $WH$ is open, we see that $\varphi(W)$ is open, as desired.
	\end{proof}
	\end{blockquote}
	Thus, we see that $\varphi|_U: U \to V$ is a bijective open map. In particular, it is a homeomorphism.
\end{proof}
For the remainder of this section, we fix $U \subset G$ and $V \subset G/H$ as above. Moreover, we fix
\begin{equation*} 
	\psi \vcentcolon= (\varphi|_U)^{-1}.
\end{equation*}
By our above discussion, $\psi:V \to U$ is a continuous function.\\
For better clarity, we shall use $1$ for the identity of $G/H$ and $1_G$ for the identity of $G.$ \\~\\
Now, we prove two key lemmas. 
\begin{lem}[Lifting Lemma] \label{lem:lift}
	If $\sigma$ is a path in $G/H$ with initial point $1,$ there is a unique path $\sigma'$ in $G$ with initial point $1_G$ such that
	\begin{equation*} 
		\varphi \circ \sigma' = \sigma.
	\end{equation*}
\end{lem}
\begin{lem}[Covering Homotopy Lemma] \label{lem:covhomot}
	If $\tau$ is also a path in $G/H$ with the initial point $1$ such that
	\begin{equation*} 
		F: \sigma \simeq \tau \rel \{0, 1\},
	\end{equation*}
	then there is a unique $F':I\times I \to G$ such that
	\begin{align*} 
		F' : \sigma' \simeq \tau' \rel \{0, 1\},\\
		\varphi \circ F' = F.
	\end{align*}
\end{lem}
(Note that $\tau'$ above is the unique path in $G$ as given by the \nameref{lem:lift}.)
\begin{proof} 
 	We prove both results together.\\
 	Let $(K, f:Y\to G/H, 0 \in K)$ be either $(I, \sigma, 0 \in I)$ or $(I \times I, F, (0, 0) \in I \times I).$ The first choice corresponds to \cref{lem:lift} and the second to \cref{lem:covhomot}. \\~\\
 	For the sake of less ugly notation, we shall use $a/b$ or $\frac{a}{b}$ to denote $ab^{-1}$ for $a, b \in G/H.$ (Note that we are fixing this to mean $ab^{-1}$ without any assumption of abelianity.)\\~\\
 	Since $K$ is compact, there exists $\epsilon > 0$ such that 
 	\begin{equation*} 
 		|k - k'| < \epsilon \implies f(k)/(f(k')) \in V,
 	\end{equation*} by \cref{lem:unifcont}.\\
 	In particular, for such $k$ and $k',$ $\psi\left(\dfrac{f(k)}{f(k')}\right)$ is defined. Fix $N \in \mathbb{N}$ large enough such that
 	\begin{equation*} 
 		|k| < N\epsilon
 	\end{equation*}
 	for all $k \in K.$ (This can be done since $K$ is bounded by $2$.)\\
 	Now, define
 	\begin{equation*} 
 		f':K \to G
 	\end{equation*}
 	by
 	\begin{align*} 
 		f'(k) \vcentcolon= &\psi\left(f(k)/f\left(\dfrac{N-1}{N}k\right)\right)\\
 		& \cdot \psi\left(f\left(\dfrac{N-1}{N}k\right)\left/f\left(\dfrac{N-2}{N}k\right)\right.\right)\\
 		& \cdots \psi\left(f\left(\dfrac{1}{N}k\right)\left/f\left(0\right)\right.\right).
 	\end{align*}
 	Then, $f'$ is continuous $K \to G,$ $f'(0) = (\varphi(1))^N = 1_G,$ and $\varphi\circ f' = f.$ To see the last point, note that $\varphi$ is a homomorphism and thus,
 	\begin{align*} 
 		(\varphi\circ f')(k) = &\varphi\left[\psi\left(f(k)/f\left(\dfrac{N-1}{N}k\right)\right)\right]\\
 		& \cdot \varphi\left[\psi\left(f\left(\dfrac{N-1}{N}k\right)\left/f\left(\dfrac{N-2}{N}k\right)\right.\right)\right]\\
 		& \cdots \varphi\left[\psi\left(f\left(\dfrac{1}{N}k\right)\left/f\left(0\right)\right.\right)\right].
 	\end{align*}
 	Now, using that $\varphi\psi(k) = k,$ we see that the fractions cancel and we are left with
 	\begin{equation*} 
 		(\varphi\circ f')(k) = f(k)/f(0) = f(k),
 	\end{equation*}
 	since $f(0) = 1_G,$ in either case.\\~\\
 	Now, suppose we had $f'': K \to G$ satisfying $f''(0) = 1_G,$ and $\varphi\circ f'' = f.$\\
 	Then, we would have $[\varphi\circ(f'/f'')](s) = \varphi(f'(s))/\varphi(f''(s)),$ since $\varphi$ is a homomorphism. However, this equals $f(s)/f(s) = 1.$\\
 	Thus, $f'/f''$ is a continuous map from $Y$ into $\ker\varphi = H.$\\
 	Since $Y$ is connected and $H$ is discrete, $f'/f''$ is a constant. Since $f'(0)/f''(0) = 1_G,$ we see that $f' = f''.$\\
 	This proves the uniqueness of $f'.$\\~\\
 	Note that in the case of the first lemma (that is $Y = I$), we have $f'(0) = 1_G$ and thus, $f'$ is the required $\sigma'.$\\~\\
 	For the case of the second lemma, we still have to prove that $F' = f'$ is the desired (relative) homotopy.\\
 	First, we show that $F'$ is indeed a (not necessarily relative) homotopy. To see this, set $\alpha(s) \vcentcolon= F'(s, 0)$ and $\beta(s) = F'(s, 1).$\\
 	Note that $\varphi\circ \alpha(s) = \varphi \circ F'(s, 0) = F(s, 0) = \sigma(s)$ and $\alpha(0) = F'(0, 0) = 1_G.$ \\
 	Since $\sigma'$ is the unique such path, we see that $\alpha = \sigma'.$\\
 	Similarly, we can conclude $\beta = \tau$ if we show that $\beta(0) = 1_G.$ By definition, we have $\beta(0) = F'(0, 1).$ \\
 	Note that $F'$ is continuous and $\varphi \circ F'$ is $1$ on $\{0\} \times I.$ Thus, $F'|_{\{0\} \times I}$ maps into $\ker \varphi = H.$ As before, we see that $F'$ is constant on $\{0\} \times I.$ Thus, $F'(0, 1) = F'(0, 0) = 1_G$ and hence, $\beta = \tau'.$\\
 	In fact, we have even proven that $F'$ is constant on $\{0\} \times I.$ This shows that $F'$ is a homotopy relative to $\{0\}.$ All that remains is to show that it is constant on $\{1\} \times I$ as well.\\
 	For that, we once again note that $\varphi\circ F' = F$ is constant on $\{1\}\times I.$ Thus, $F'|_{\{1\}\times I}$ maps into a coset of $\ker \varphi = H.$ Since the coset is homeomorphic to $H,$ it must be discrete as well. This proves that $F'$ is constant on $\{1\} \times I$ as well, proving that
 	\begin{equation*} 
 		F' : \sigma' \simeq \tau' \rel \{0, 1\}. \qedhere
 	\end{equation*}
 \end{proof} 

\begin{cor} \label{cor:endpthomot}
	The end point of $\sigma'$ only depends on the homotopy class of $\sigma.$\\
	In particular, if $\sigma$ is a loop at $1,$ then $\sigma'(1) \in H.$
\end{cor}
\begin{proof} 
	Let $\sigma, \tau$ be paths in the same homotopy class. Let $F:\sigma \simeq \tau \rel \{0, 1\}$ be a (relative) homotopy.\\
	Then, $F'$ is a homotopy from $\sigma'$ to $\tau'$ relative to $\{0, 1\}.$\\
	In particular, we have $\sigma'(1) = F(1, 0) = F(1, 1) = \tau'(1).$ This proves the first statement.\\~\\
	For the second statement, note that $\varphi\circ\sigma'(1) = \sigma(1) = 1$ and thus, $\sigma'(1) \in \ker\varphi = H.$
\end{proof}

Now, we have the following theorem.
\begin{thm}
	If $G$ is a simply connected topological group, $H$ a discrete normal subgroup, then
	\begin{equation*} 
		\pi_1(G/H, 1) \cong H.
	\end{equation*}
\end{thm}
\begin{proof} 
	Using \cref{cor:endpthomot}, we define $\chi:\pi_1(G/H, 1) \to H$ by
	\begin{equation*} 
		\chi([\sigma]) = \sigma'(1).
	\end{equation*}
	\begin{blockquote}
		\textbf{Claim 1.} $\chi$ is a homomorphism.
		\begin{proof} 
			Let $[\sigma], [\tau] \in \pi_1(G/H, 1).$\\
			Let $h_1 = \sigma'(1)$ and $h_2 = \tau'(1).$ (Again, we see that these are well-defined and elements of $H$ by \cref{cor:endpthomot}.) \\
			Let $\tau''$ be the path from $h_1$ to $h_1h_2$ in $G$ given by
			\begin{equation*} 
				\tau''(s) = h_1\tau'(s).
			\end{equation*}
			(Note that $\tau''(0) = \tau'(0)h_1 = 1_Gh_1 = h_1$ and $\tau''(1) = h_1\tau'(1) = h_1h_2.$)\\
			Note that
			\begin{equation*} 
				(\varphi\circ\tau'')(s) = \varphi(\tau'(s)h_1) = \varphi(\tau'(s))\varphi(h_1) = \tau(s).
			\end{equation*}
			(Note that $\varphi(h_1) = 1$ since $h_1 \in H = \ker\varphi.$)\\
			Since, $\sigma'(1) = \tau''(0) = h_1,$ we can consider the path $\tau''\sigma'$ in $G.$ Note that
			\begin{equation*} 
				\varphi\circ(\tau''\sigma')(s) = \begin{cases}
					\varphi(\sigma'(2s)) & 0 \le 2s \le 1\\
					\varphi(\tau''(2s - 1)) & 1 \le 2s \le 2.
				\end{cases} = (\sigma\tau)(s).
			\end{equation*}
			Thus, $\tau''\sigma'$ is the unique lift of $\sigma\tau$ as given by the \nameref{lem:lift}. \\
			Thus,
			\begin{equation*} 
				\chi([\sigma][\tau]) = \chi[\sigma\tau] = (\tau''\sigma')(1) = h_1h_2 = \chi[\sigma]\chi[\tau]. \qedhere
			\end{equation*}

		\end{proof}
	\end{blockquote}
	Now, we show that $\chi$ is bijective.
	\begin{blockquote}
		\textbf{Claim 2.} $\chi$ is injective.
		\begin{proof} 
			It suffices to show that $\ker \chi$ is trivial.\\
			Let $[\sigma] \in \ker\chi.$ Then, $\sigma'(1) = 1_G.$\\
			In other words, $\sigma'$ is a loop at $1_G$ in $G.$ Since $G$ is simply connected, $\sigma'$ is path homotopic to a constant loop. We may choose the constant loop to be $e_{1_G}.$\\
			Thus, $\sigma' \simeq e_{1_G} \rel \{0, 1\}.$\\
			Applying $\varphi,$ we get that $\sigma \simeq e_1 \rel \{0, 1\}$ or $[\sigma] = [e_1],$ the identity of $\pi_1(G/H, 1).$	
		\end{proof}
	\end{blockquote}
	\begin{blockquote}
		\textbf{Claim 3.} $\chi$ is surjective.	
		\begin{proof} 
			Let $h \in H$ be arbitrary.\\
			Since $G$ is simply-connected, it is pathwise connected. Let $\sigma'$ be path from $1_G$ to $h$ in $G.$\\
			Then, $\varphi\circ\sigma':I\to G/H$ is a loop at $1$ in $G/H$ with
			\begin{equation*} 
				\chi[\sigma] = \sigma'(1) = h. \qedhere
			\end{equation*}
		\end{proof}
	\end{blockquote}
	With that, we are done!
\end{proof}
\begin{cor}
	The fundamental group of $S^1$ is (isomorphic to) $\mathbb{Z}.$
\end{cor}
(Since $S^1$ is pathwise connected, we need not care about base point.)\\
In particular, the above corollary shows that $S^1$ is not simply connected. This is our first example of a non-simply connected space.
\begin{cor}
	The fundamental group of a torus is (isomorphic to) $\mathbb{Z} \times \mathbb{Z}.$
\end{cor}
\begin{proof} 
	The torus is (homeomorphic to) $(\mathbb{R} \times \mathbb{R})/(\mathbb{Z} \times \mathbb{Z}).$
\end{proof}
Note that the torus is also homeomorphic to $S^1 \times S^1.$ Using this, we could've calculated the fundamental group in a different way with the help of the following proposition.
\begin{prop}
	Given spaces $X, Y, x_0 \in X, y_0 \in Y,$ we have
	\begin{equation*} 
		\pi_1(X \times Y, (x_0, y_0)) \cong \pi_1(X, x_0) \times \pi_1(Y, y_0).
	\end{equation*}
\end{prop}
\begin{proof} 
	The isomorphism is obtained as follows. First, consider the maps of pointed topological spaces given by the projections
	\begin{center}
		\begin{tikzcd}
			(X, x_0) &  & (X \times Y, (x_0, y_0)) \arrow[ll, "p_X"'] \arrow[rr, "p_Y"] &  & (Y, y_0).
		\end{tikzcd}
	\end{center}
	These maps induce the homomorphisms
	\begin{center}
		\begin{tikzcd}
			\pi_1(X, x_0) &  & \pi_1(X \times Y, (x_0, y_0)) \arrow[ll, "(p_X)_*"'] \arrow[rr, "(p_Y)_*"] &  & \pi_1(Y, y_0).
		\end{tikzcd}
	\end{center}
	Using the universal property of product of groups, we get a homomorphism $\langle (p_X)_*, (p_Y)_*\rangle$ as follows
	\begin{center}
		\begin{tikzcd}
		{\pi_1(X, x_0)} &  & {\pi_1(X \times Y, (x_0, y_0))} \arrow[ll, "(p_X)_*"'] \arrow[rr, "(p_Y)_*"] \arrow[dddd, "{\langle (p_X)_*, (p_Y)_*\rangle}" description] &  & {\pi_1(Y, y_0)} \\
		&&&&\\&&&&\\&&&&\\
		&&{\pi_1(X, x_0) \times \pi_1(Y, y_0)} \arrow[lluuuu, two heads] \arrow[rruuuu, two heads]                                         &  &      
		\end{tikzcd}
	\end{center}
	such that the diagram commutes. (The $\twoheadrightarrow$s are the usual projections.)\\
	Let $\varphi \vcentcolon= \langle (p_X)_*, (p_Y)_*\rangle.$ We show that this is an isomorphism by constructing an inverse $\psi:\pi_1(X, x_0) \times \pi_1(Y, y_0) \to \pi_1(X \times Y, (x_0, y_0))$ .\\~\\
	%
	Any element of $\pi_1(X, x_0) \times \pi_1(Y, y_0)$ is of the form $([\sigma], [\tau])$ for some loop $\sigma$ (resp., $\tau$) at $x_0$ (resp., $y_0$) in $X$ (resp., $Y$).\\
	We define $\psi([\sigma], [\tau])$ as the class of the loop at $(x_0, y_0)$ in $X \times Y$ given by
	\begin{equation*} 
		(\sigma, \tau)(s) \vcentcolon= (\sigma(t), \tau(t)), \quad t \in I.
	\end{equation*}
	That is, $\psi([\sigma], [\tau]) = [(\sigma, \tau)].$ One can verify that this is well-defined.\\
	(That is, if $\sigma \simeq \sigma'$ and $\tau \simeq \tau',$ then $(\sigma, \tau) \simeq (\sigma', \tau'),$ all relative to $\{0, 1\}.$)\\
	Now, one can verify that $\varphi\circ\psi$ and $\psi\circ\varphi$ are both the respective identities. \\~\\
	%
	Alternately, as a more category theoretic proof, one can verify that the following diagram commutes.
	\begin{center}
		\begin{tikzcd}
		{\pi_1(X, x_0)} &  & {\pi_1(X \times Y, (x_0, y_0))} \arrow[ll, "(p_X)_*"'] \arrow[rr, "(p_Y)_*"] &  & {\pi_1(Y, y_0)} \\
		&&&&\\&&&&\\&&&&\\
		&&{\pi_1(X, x_0) \times \pi_1(Y, y_0)} \arrow[uuuu, "{\psi}" description] \arrow[lluuuu, two heads] \arrow[rruuuu, two heads]                                         &  &      
		\end{tikzcd}
	\end{center}
	Thus, given any object and arrows $\pi_1(X, x_0) \longleftarrow Z \longrightarrow \pi_1(Y, y_0),$ we get an arrow $\eta:Z \longrightarrow \pi_1(X, x_0) \times \pi_1(Y, y_0)$ such that the following diagram commutes.
	\begin{center}
		\begin{tikzcd}
		{\pi_1(X, x_0)} &  & {\pi_1(X \times Y, (x_0, y_0))} \arrow[ll, "(p_X)_*"'] \arrow[rr, "(p_Y)_*"] &  & {\pi_1(Y, y_0)} \\
		&&&&\\&&&&\\&&&&\\
		&&{Z} \arrow[uuuu, "{\psi\circ\eta}" description] \arrow[lluuuu] \arrow[rruuuu]                                         &  &      
		\end{tikzcd}
	\end{center}
	That is, $\pi_1(X \times Y, (x_0, y_0))$ satisfies the universal mapping property of a product. Since products are unique up to isomorphism, we see that
	\begin{equation*} 
		\pi_1(X \times Y, (x_0, y_0)) \cong \pi_1(X, x_0) \times \pi_1(Y, y_0). \qedhere
	\end{equation*}
\end{proof}

\begin{defn}[Retract]
	A subset $Y$ of a topological space $X$ is called a \emph{retract} if there exists a map $r:X \to Y$ such that
	\begin{equation*} 
		ri = \id_Y,
	\end{equation*}
	where $i:Y \hookrightarrow X$ is the inclusion map.
\end{defn}
\begin{thm}
	The circle $S^1$ is not a retract of the closed disc $D^2.$
\end{thm}
\begin{proof} 
	We prove a stronger result that $ri \simeq \id_{S^1}$ is impossible for any map $r:X \to Y.$\\
	Indeed, assume the contrary and let $r:X \to Y$ be a map such that $ri \simeq \id_{S^1}.$ Then, $(ri)_* = r_*i_*$ is an isomorphism, by \cref{cor:homsameiso}.\\
	However, note that 
	\begin{center}
		\begin{tikzcd}
			\pi_1(S^1) \arrow[rr, "i_*"] \arrow[rrdd, "\id"'] &  & \pi_1(D^2) \arrow[dd, "r_*"] \\&&\\
			&  & \pi_1(S^1)                  
		\end{tikzcd}
	\end{center}
	Recalling that $\pi_1(S^1) \cong \mathbb{Z}$ and $\pi_1(D^2) = \{1\},$ we see that the above is impossible since $\mathbb{Z} \to \{1\} \to \mathbb{Z}$ cannot be an isomorphism. \\
	(There is neither any injection $i_* : \mathbb{Z} \to \{1\}$ nor any surjection $r_* : \{1\} \to \mathbb{Z}.$)
\end{proof}
\begin{cor}[Special Brouwer Fixed Theorem]
	Any continuous map of the closed disc into itself has a fixed point.
\end{cor}
\begin{proof} 
	Suppose $f:D^2 \to D^2$ has no fixed point. We define $r:D^2 \to S^1$ as follows:\\
	Take the ray joining $f(x)$ to $x$ and extend it until it reaches the circle $S^1.$ Call this point on $S^1$ $r(x).$\\
	Clearly, if $x \in S^1,$ then $r(x) = x.$ Thus, $ri = \id_{S^1},$ a contradiction to the previous theorem.
\end{proof}
\emph{Remark.} This is a special case of Brouwer's fixed point theorem for $n = 2.$ The case $n = 1$ is simple by considering the function $g(x) = f(x) - x$ and noting that $g(-1) \ge 0$ and $g(1) \le 1$, thereby giving us that $g(c) = 0$ for some $c \in D^1 = [-1, 1].$\\~\\
Note that it must be justified that the $r$ defined above is indeed continuous. This is a fairly straightforward calculation. An outline is as follows:\\
Consider the ray $\zeta_x$ given by $\zeta_x(t) = (1 - t)f(x) + tx$ for $t \ge 0.$ We need a solution $t > 0$ for $\|\zeta_x(t)\| = 1.$ This turns out to be equivalent to solving
\begin{equation*} 
	\|x - f(x)\|^2 t^2 + 2(\langle x, f(x)\rangle - \|f(x)\|^2) + \|f(x)\|^2 - 1 = 0.
\end{equation*} 
By our assumption, $x \neq f(x)$ and thus, the above is a genuine quadratic expression for all $x.$ Moreover, using $\|f(x)\|^2 \le 1,$ one can show that the above has one unique positive root, call this $t(x).$ Clearly, $x \mapsto t(x)$ is continuous. (Quadratic formula.)\\
Thus, $r(x) = (1 - t(x))f(x) + t(x)x$ is a continuous function of $x.$

\begin{thm}
	Let $X$ be a topological space and $x \in X.$ Suppose $\mathcal{U}$ is an open cover of $X$ with the following properties:
	\begin{enumerate}
		\item $U_i \cap U_j$ contains $x$ and is pathwise connected for all $U_i, U_j \in \mathcal{U}$,
		\item $U$ is simply connected for all $U \in \mathcal{U}.$
	\end{enumerate}
	Then, $X$ is simply connected.
\end{thm}
\begin{proof} 
	It is clear that $X$ is pathwise connected since it is the union of pathwise connected sets with a point in common. Thus, we just need to show that any loop is path homotopic to a constant loop. Of course, since $X$ is pathwise connected, we can choose any base point of our choice. We choose the point $x.$ \\~\\
	Let $\sigma:I \to X$ be any loop at $x.$\\
	By the Lebsgue number lemma, there exists a subdivision
	\begin{equation*} 
		[\sigma] = [\sigma_1]*\cdots*[\sigma_n]
	\end{equation*}
	such that each $\sigma_i(I)$ is contained in some $U_i \in \mathcal{U}.$ \\
	Now, we define the paths $\tau_1, \ldots, \tau_{n+1}$ as follows:
	\begin{itemize}
		\item $\tau_1$ and $\tau_{n+1}$ are the constant loops at $x.$
		\item For $1 < i \le n,$ $\tau_i$ is any path joining $\sigma_i(0)$ to $x$ lying in $U_{i-1} \cap U_i.$ \\
		We can do so because $\sigma_i(0) = \sigma_{i_1}(1)$ is a point in $U_{i-1} \cap U_i.$ Since this intersection contains $x$ and is pathwise connected, we are done.
	\end{itemize}
	Now, note that the path $\tau_i^{-1}\sigma_i\tau_{i+1}$ is a loop that lies in $U_i$ for all $1 \le i \le n.$ Since $U_i$ is simply connected, we see that $[\tau_i^{-1}\sigma_i\tau_{i+1}]$ is the constant element $[e_{x}] \in \pi_1(X).$\\
	Moreover, observe the following product taken over all $1 \le i \le n$ telescopes. That is,
	\begin{align*} 
		[\sigma] &= [\sigma_1]\cdots[\sigma_n]\\
		&= \prod_{i = 1}^{n}[\tau_i^{-1}\sigma_i\tau_{i+1}]\\
		&= \prod_{i = 1}^{n}[e_x]\\
		&= [e_x],
	\end{align*}
	as desired. (Note that $[\tau_1^{-1}] = [\tau_{n+1}] = [e_x]$ as well.)
\end{proof}
\begin{prop}
	The space $S^n$ is simply connected for $n \ge 2.$
\end{prop}
\begin{proof} 
	We apply the above theorem with $X = S^n,$ $\mathcal{U} = \{U, V\}$ with $U = S^n\setminus\{(1, 0, \ldots, 0)\}$ and $V = S^n\setminus\{(-1, 0, \ldots, 0)\}.$\\
	(In other words, $U$ is $S^n$ with one point removed and $V$ is $S^n$ with the opposite point removed.)\\
	It is clear that $\mathcal{U}$ is open cover. Recall that $\mathbb{R}^n$ is homeomorphic to $S^n$ with a point removed.\\
	Thus, both $U$ and $V$ are simply connected since $\mathbb{R}^n$ is.\\
	Moreover, $U \cap V$ is homeomorphic to $\mathbb{R}^n$ with two points removed. Since $n \ge 2,$ this space is path connected.\\
	Thus, $\mathcal{U}$ satisfies the criterion of the previous theorem and the result follows.
\end{proof}
%\\
%
\section{Covering spaces}
%
In this section, we try to generalise the ideas of earlier. The previous section let us calculate $\pi_1(X)$ in the particular case that $X$ was a topological group (and could be realised as a quotient group in a particular manner).\\
In section, we shall consider $X$ which is not necessarily a group but represent it as a quotient space of a simply connected space $\tilde{X}.$ As before, we shall work in the case that the fibers of $\tilde{X} \to X$ are discrete.\\
Towards this end, we have the following definition.

\begin{defn}[Covering space]
	$E \overset{p}{\longrightarrow} X$ is a \emph{covering space of $X$} if every $x \in X$ has an open neighbourhood $U$ such that $p^{-1}(U)$ is a disjoint union of open sets $S_i$ in $E,$ each of which is mapped homeomorphically onto $U$ by $p.$ Such $U$ are said to be \emph{evenly covered,} and the $S_i$ are called \emph{sheets} over $U.$
\end{defn}
\begin{prop}[Consequences]
	From the above definition, the following results follow.
	\begin{enumerate}
		\item The fiber $p^{-1}(x)$ over any point is discrete;
		\item $p$ is a local homeomorphism;
		\item $p$ maps $E$ onto $X$ and $X$ has the quotient topology from $E.$
		\item If $E$ is locally pathwise connected, then so is $X.$
	\end{enumerate}
\end{prop}
\begin{proof} 
	\phantom{hi}
	\begin{enumerate}
		\item Let $x \in X$ and $U$ be a neighbourhood of $x$ which is evenly covered. Then, $p^{-1}(U) = \displaystyle\bigsqcup_{i \in I} S_i.$\\
		Let $y \in p^{-1}(x).$ Then, $y \in S_i$ for some $i_0 \in I.$ Moreover, since $p:S_{i_0} \to U$ is homeomorphism, it is one-one and thus, $p(y') \neq x$ for any $y \neq y' \in S_{i_0}.$\\
		In other words, $S_{i_0} \cap p^{-1}(x) = \{y\}$ and thus, $\{y\}$ is open in $p^{-1}(x).$ (Since $S_{i_0}$ was open.)\\
		This shows that $p^{-1}(x)$ is discrete.
		\item By definition, we need to show that given any $e \in E,$ there exists a neighbourhood $V$ of $e$ such that $p(V)$ is open in $X$ and $p|_V:V \to p(V)$ is a homeomorphism.\\~\\
		To this end, let $e \in E$ be arbitrary and let $x = p(e).$\\
		Let $U$ an evenly covered neighbourhood of $x$ and $S_{i_0}$ be the sheet (over $U$) containing $e.$\\
		By definition (of covering spaces), we have that $p_{S_{i_0}}$ is a homeomorphism, as desired.
		\item The fact that $p$ is onto follows straight from the definition. (Every $x \in X$ has a neighbourhood $U$ which is evenly covered and thus, a sheet maps onto $U$ and in particular, something gets mapped to $x \in U$.)\\~\\
		Showing that $X$ has the quotient topology from $E$ is the same as showing that $p$ is a quotient map. Let $U \subset X.$ We need to show that $p^{-1}(U)$ is open iff $U$ is open. (We already know that $p$ is surjective.)\\
		If $U$ is open, then $p^{-1}(U)$ is open since $p$ is continuous. (It is a local homeomorphism.)\\
		Conversely, let $p^{-1}(U)$ be open. We show that $U$ is open. To this end, let $x \in U.$ Consider any $e \in E$ such that $p(e) = x.$ Then, $e \in p^{-1}(U).$ Since $p$ is a local homeomorphism and $p^{-1}(U)$ is open, we can find a neighbourhood $V$ of $e$ contained in $p^{-1}(U)$ such that $p(V)$ is open.\\
		However, note that $x \in p(V) \subset U.$ This shows that $x$ is an interior point and thus, $U$ is open. (Since $x$ was arbitrary.)
		\item Let $x \in X$ and $U$ be an arbitrary neighbourhood of $x.$\\
		Choose a neighbourhood $U'$ of $x$ which is evenly covered and let $S'$ be a sheet over $U'.$ Then, $p|_{S'}$ is a homeomorphism. \\
		Let $W = U \cap U'.$ Consider $p|_{S'}^{-1}(W);$ this is an open subset of $S'$ and hence, of $E.$\\
		Since $E$ is locally pathwise connected, we can find a pathwise connected neighbourhood $V \subset p|_{S'}^{-1}(W)$ of $p|_{S'}^{-1}(x) \in S'.$\\
		Then, its image $p_{S'}(V) \subset W \subset U$ is a neighbourhood of $x$ and is pathwise connected. (Since it is homeomorphic to $V.$)\\
		This shows that $X$ is locally pathwise connected. \qedhere
	\end{enumerate}
\end{proof}

Thus, covering spaces is the analogue of the previous section that we described earlier.\\
We now give the analogues of \cref{lem:lift} and \cref{lem:covhomot}.

\begin{thm}[Unique lifting theorem] \label{thm:uniquelift}
	Let $(E, e_0) \overset{p}{\longrightarrow} (X, x_0)$ be a covering space with base points, $(Y, y_0) \overset{f}{\longrightarrow} (X, x_0)$ any map. Assume that $Y$ is connected. \emph{If} there is a map $(Y, y_0) \overset{E, e_0}{\longrightarrow}$ such that $pf' = f,$ \emph{then} it is unique.
\end{thm}
(Note that this is different from \cref{lem:lift} since we don't guarantee the \emph{existence} of an $f'.$)
\begin{proof} 
	With everything as in the lemma, assume that $f'':(Y, y_0) \to (E, e_0)$ is also a map such that $pf'' = f.$\\
	We show that $f' = f''.$\\~\\
	Define $A \subset Y$ as
	\begin{equation*} 
		A \vcentcolon= \{y \in Y \mid f'(y) = f''(y)\}.
	\end{equation*}
	Note that $A \neq \emptyset$ since $y_0 \in A.$ (Since $f'(y_0) = e_0 = f''(y_0),$ by assumption.)\\
	We will show that $A$ is both open and closed. Then, since $Y$ is connected and $A$ is nonempty, it will follow that $A = Y.$ In turn, that will show that $f' = f''.$\\
	\begin{blockquote}
		\textbf{Claim 1.} $A$ is open.
		\begin{proof} 
			Let $y \in A.$ Let $U$ be an evenly covered neighbourhood of $f(y) = pf'(y).$\\
			Then, $f'(y)$ lies on some sheet $S$ over $U.$ Since $y \in A,$ we have $f'(y) = f''(y).$ Thus, the set $B \vcentcolon= f'^{-1}(S) \cap f''^{-1}(S)$ is an open set containing $y.$\\
			\begin{blockquote}
				\textbf{Subclaim 1.1.} $B \subset A.$
				\begin{proof} 
					Let $y_1 \in B.$ Then, $y \in f'^{-1}(S) \cap f''^{-1}(S).$ \\
					That is $f'(y_1) \in S \ni f''(y_1).$\\
					Note that $p|_S$ is a homeomorphism and in particular, one-one. Since $pf'(y_1) = f(y_1) = pf''(y_1),$ we see that $f'(y_1) = f''(y_1)$ and hence, $y_1 \in A.$
				\end{proof}
			\end{blockquote}
			Thus, we have seen that given any $y \in A,$ there exists an open set $B$ with $y \in B \subset A,$ showing that $A$ is open.
		\end{proof}
	\end{blockquote}
	\begin{blockquote}
		\textbf{Claim 2.} $A$ is closed.
		\begin{proof} 
			We show that $Y\setminus A$ is open. Let $y \in Y\setminus A.$\\
			As before, let $U$ be an evenly covered neighbourhood of $f(y) = pf'(y).$\\
			Since $p$ restricted to sheets is injective and $pf'(y) = pf''(y),$ it follows that $f'(y)$ and $f''(y)$ lie on different sheets, say $S_1$ and $S_2,$ respectively.\\
			Let $B' \vcentcolon= f'^{-1}(S_1) \cap f''^{-1}(S_2).$ Clearly, $y \in B'.$\\
			\begin{blockquote}
				\textbf{Subclaim 2.1.} $B' \subset X\setminus A.$
				\begin{proof} 
					Let $y_1 \in B'.$ \\
					Then, $f'(y_1) \in S_1$ and $f''(y_2) \in S_2.$ Since $S_1$ and $S_2$ are disjoint, the claim follows.
				\end{proof}
			\end{blockquote}
			The above subclaim proves that $X\setminus A$ is open, as earlier.
		\end{proof}
	\end{blockquote}
	Thus, we are done.
\end{proof}
\begin{thm}[Path Lifting Theorem] 
	For $(E, e_0) \overset{p}{\longrightarrow} (X, x_0)$ a covering space with base points, if $\sigma$ is a path in $X$ with initial point $x_0,$ there is a unique path $\sigma_{e_0}'$ in $E$ with initial point $e_0$ such that $p\sigma_{e_0}' = \sigma.$
\end{thm}
\begin{proof} 
	Note that $\sigma$ is actually a pointed map $(I, 0) \overset{\sigma}{\longrightarrow} (X, x_0)$ and $I$ is connected. Thus, uniqueness of $\sigma_{e_0}'$ follows from \nameref{thm:uniquelift}.\\~\\
	\emph{Special case}: The whole space $X$ is evenly covered. \\
	Let $S$ be the sheet (over $X$) containing $e_0.$ Then, $p|_S : S \to X$ is a homeomorphism. Let $\psi:X \to S$ be the inverse to this.\\
	Then, $\sigma_{e_0}' = \psi\circ\sigma$ is the desired map.\\
	Note that $p\sigma_{e_0}' = p\psi\sigma = \sigma$ and $\psi\sigma(0) = \psi(x_0) = e_0,$ since $p(e_0) = x_0.$ Thus, $\sigma_{e_0}'$ indeed is a pointed map.\\~\\
	\emph{General case}: Note that $\sigma(I) \subset X$ is compact. Thus, we can find a finite open cover $\{U_i\}_{i = 0}^{n-1}$ of $\sigma(I)$ such that each $U_i$ is evenly covered.\\
	Thus, by the Lebesgue number lemma, we can find a partition
	\begin{equation*} 
		0 = t_0 < t_1 < \cdots < t_n = 1
	\end{equation*}
	such that $\sigma([t_i, t_{i + i}])$ lies in the evenly covered neighbourhood $U_i$ of $\sigma(t_i)$ for all $0 \le i < n.$\\
	(Well, not exactly but we can renumber $U_i$ wlog so that they satisfy the above condition.)\\
	Thus, note that for each ``sub-path'' $s|_{[t_i, t_{i + 1}]} : [t_i, t_{i + 1}] \to U_i,$ we can apply the first case.\\
	In particular, for $i = 0,$ we lift $s|_{[0, t_1]}$ to a path $\sigma_1':[0, t_i] \to E$ such that $\sigma_1'(0) = e_0.$\\
	Assume, as induction, that we have lifted $\sigma|_{[0, t_i]}$ to a map $\sigma_i':[0, t_i] \to E$ such that $\sigma_i(0) = e_0.$ ($0 \le i < n - 1.$)\\
	Also, observe that $p\sigma_i'(t_i) = \sigma(t_i).$\\
	Then, we can lift $\sigma|_{[t_i, t_{i + 1}]}$ to a path $\tau_i:[t_i, t_{i + 1}] \to E$ with $\tau_i(t_i) = \sigma_i'(t_{i}).$ (This is because for the lifting theorem, all we used was that $e_0$ was a point that gets mapped to $x_0$ under $p$. By our previous observation, we see that $\sigma_i(t_i) \overset{p}{\mapsto}\sigma(t_i)$ and thus, we can lift a path preserving initial points like that.)\\
	Thus, we get a path $\sigma_{i+1}':[0, t_{i + 1}] \to E$ given by joining $\sigma_i$ and $\tau_i.$\\~\\
	Thus, by induction, we get a path $\sigma_n'$ which is our desired $\sigma_{e_0}'.$	
\end{proof}
% %
% \begin{thm}[Covering Homotopy Theorem] \label{thm:covhomot}
% 	Let $(E, e_0) \overset{p}{\longrightarrow}(X, x_0)$ be a covering space as above.\\
% 	Let $(Y, y_0)$ be a connected (pointed) topological space and $f:(Y, y_0) \to (X, x_0)$ a map which has a lifting $f':(Y, y_0) \to (E, e_0).$ Then, any homotopy $F:Y\times I \to X$ with $F(y, 0) = f(y)$ for all $y \in Y$ can be lifted to a homotopy $F':Y \times I \to E$ with $F'(y, 0) = f'(y)$ for all $y \in Y.$
% \end{thm}
% \begin{proof} 
% 	We prove this is three steps.
% 	\begin{enumerate}
% 		\item Assume the case that $X$ is evenly covered.\\
% 		Let $S$ be the sheet (over $X$) containing $e_0$ and $\psi:X \to S$ be the inverse to the homeomorphism $p|_S.$\\
% 		Define $F' = \psi\circ F.$ Clearly, $F'$ is a lift. We now show that $F'(y, 0) = f'(y)$ for all $y \in Y.$\\~\\
% 		To this end, define $\alpha:Y \to X$ by $\alpha(y) = F'(y, 0).$\\
% 		Note that $p\circ\alpha(y_0) = p\circ F'(y_0, 0) = F(y_0, 0) = f(y_0) = x_0.$\\
% 		Note that, by definition, $\alpha$ must map into $S,$ the sheet containing $e_0.$ Thus, $\alpha(y_0) \in S$ is an element such that $p(\alpha(y_0)) = x_0.$ Since $p|_S$ is one-one and $p(e_0) = x_0,$ we see that
% 		\begin{equation*} 
% 			\alpha(y_0) = e_0.
% 		\end{equation*}
% 		Moreover, note that $p\alpha(y) = pF'(y, 0) = F(y, 0) = f(y)$ for all $y \in Y.$\\
% 		Thus, $\alpha:(Y, y_0) \to (E, e_0)$ is a map such that $p\alpha = f.$ Since $f'$ is also one such, it follows that $f' = \alpha,$ by \nameref{thm:uniquelift}.\\~\\
% 		Thus, we have
% 		\begin{equation*} 
% 			F'(y, 0) = \alpha(y) = f'(y), \text{ for all } y \in Y,
% 		\end{equation*}
% 		as desired.
% 		\item 
% 	\end{enumerate}
% \end{proof}
\begin{thm}[Covering Homotopy Theorem]
	Let $(E, e_0) \overset{p}{\longrightarrow} (X, x_0)$ be a covering map as before. Let $F:I \times I \to X$ be a map with $F(0, 0) = x_0.$\\
	There is a unique lifting of $F$ to a continuous map
	\begin{equation*} 
		F':I \times I \to E
	\end{equation*}
	such that $F'(0, 0) = e_0.$ Moreover, if $F$ is a path homotopy, then $F'$ is a path homotopy.
\end{thm} 
\begin{proof} 
	We first define $F'(0, 0) = e_0.$ We will construct $F'$ piece-wise.\\
	First, we use the preceding theorem to extend $F$ to the left edge $\{0\} \times I$ and bottom edge $I \times \{0\}.$ \\
	Now, choose subdivision
	\begin{align*} 
		0 = s_0 < s_1 < \cdots < s_m = 1,\\
		0 = t_0 < t_1 < \cdots < t_n = 1
	\end{align*}
	such that each rectangle 
	\begin{equation*} 
		I_i \times J_i = [s_{i - 1}, s_i] \times [t_{i - 1}, t_i] 
	\end{equation*}
	is mapped by $F$ into an open subset of $X$ which is evenly covered by $p.$ (This is for all $1 \le i \le m$ and $1 \le j \le n.$ Such a subdivision exists by the Lebesgue number lemma.)\\
	We now define the lift $F'$ inductively. First we define it on $I_1 \times J_1,$ continuing with the other rectangles $I_i \times J_1$ in the bottom row from left to right, then with the rectangles $I_i \times J_2$ in the second row from left to and right, and so on.\\~\\
	In general, given $i_0$ and $j_0,$ we assume that $F'$ has been defined on set
	\begin{equation*} 
		A = \bigcup_{\substack{j < j_0\\1 \le i \le n}}(I_i \times J_j) \cup \bigcup_{i < i_0}(I_i \times J_{j_0}) \cup \left(\{0\} \times I\right) \cup \left(I \times \{0\}\right).
	\end{equation*}
	(That is, $A$ is the union of the left and bottom edges along with the ``previous'' rectangles.)\\
	We also assume that $F'$ defined on $A$ so far is a continuous lifting of $F|_A.$ Using this, we define $F'$ on $I_{i_0} \times J_{j_0}$ such that it's continuous on $A \cup (I_{i_0} \times J_{j_0}).$\\~\\
	Choose an open set $U$ which is evenly covered by $p$ and contains $I_{i_0} \times J_{j_0}.$ (Such a $U$ exists by our construction of the subdivision.)\\
	Let $\{S_\alpha\}$ be the set of sheets, each $S_\alpha$ being mapped homeomorphically onto $U$ by $p.$\\
	Note that $F'$ is already defined on the subset of $I_{i_0} \times J_{j_0}$ given by $C = A \cap (I_{i_0} \times J_{j_0}).$ This subset is \emph{connected} and hence, $F'(C),$ being connected must lie entirely in one sheet.\\
	Let $S_0$ be this sheet. Let $p_0 \vcentcolon= p|_{S_0}.$ Then,
	\begin{equation*} 
		p_0 : S_0 \to U
	\end{equation*}
	is a homeomorphism. Moreover, for $x \in C,$ we have
	\begin{equation*} 
		p_0(F'(x)) = p(F'(x)) = F(x),
	\end{equation*}
	since $F'$ is a lifting of $F|_A.$ Thus, for $x \in C,$ we have that
	\begin{equation*} 
		F'(x) = p_0^{-1}(F(x)).
	\end{equation*}
	Thus, if we now define
	\begin{equation*} 
		F'(y) = p_0^{-1}(F(y))
	\end{equation*}
	for $y \in I_{i_0} \times J_{j_0},$ we see that $F'$ must be continuous on $A \cup (I_{i_0}) \times (J_{j_0}),$ by the pasting lemma.\\
	Moreover, it is clearly a lift of $F|_{A \cup (I_{i_0} \times J_{j_0})}$ as well. Thus, it satisfies our inductive hypothesis and we may carry out this process and define $F'$ on all of $I \times I.$\\~\\
	To see uniqueness, note that we were forced to define $F'(0, 0) = e_0.$ Thus, considering $(Y, y_0)$ with $Y = I \times I$ and $y_0 = (0, 0),$ appealing to the \nameref{thm:uniquelift}, we see that at each step, there is a unique lift to $I_{i_0} \times J_{j_0}.$ Thus, defining $F'(0, 0)$ uniquely determines $F'.$\\~\\
	Now, suppose that $F$ is a path homotopy. (Note that since we are not saying anything about the two paths between which it is a homotopy, all that matters is that $F$ is constant on the vertical edges.)\\
	Then, the map $F$ carries $\{0\} \times I$ onto a singleton $\{x_0\}.$ Since $pF' = F,$ we must have that
	\begin{equation*} 
		(pF')(\{0\} \times I) = \{x_0\}.
	\end{equation*}
	In other words, $F'$ carries $\{0\} \times I$ into $p^{-1}(x_0).$ However, note that $\{0\} \times I$ is connected whereas $p^{-1}(x_0)$ is discrete. Thus, $F'$ must be constant on $\{0\} \times I.$\\
	Similarly, it must be constant on $\{1\} \times I$ as well, proving the result.
\end{proof}

\begin{thm}
	Let $(E, e_0) \overset{p}{\longrightarrow} (X, x_0)$ be a covering map as before. Let $f$ and $g$ be two paths in $X$ from $x_0$ to $x_1;$ let $f'$ and $g'$ be their respective liftings to paths in $E$ beginning at $e_0.$ If $f$ and $g$ are path homotopic, then so are $f'$ and $g'.$ In particular, $f'$ and $g'$ have the same terminal point.
\end{thm}
\begin{proof} 
	Let $F:f\simeq g \rel \{0, 1\}$ be a path homotopy from $f$ to $g.$\\
	Let $F'$ be given as in the preceding lemma. We wish to show that the bottom edge is $f'$ and top $g'.$\\
	To this end, define $\alpha, \beta:I\to E$ as
	\begin{align*} 
		\alpha(s) &\vcentcolon= F'(s, 0),\\
		\beta(s) &\vcentcolon= F'(s, 1).
	\end{align*}
	We show that $\alpha = f'$ and $\beta = g'.$\\
	Note that $\alpha(0) = F'(0, 0) = e_0 = F'(0, 1) = \beta(0).$\\
	Moreover, $p(\alpha(s)) = p(F'(s, 0)) = F(s, 0) = f(s)$ and similarly, $p(\beta(s)) = g(s).$\\
	Thus, $\alpha$ and $\beta$ are some lifts of $f$ and $g$ starting at $e_0.$ By the \nameref{thm:uniquelift}, we are done.
\end{proof}
\begin{cor}
	$p_* : \pi_1(E, e_0) \to \pi_1(X, x_0)$ is a monomorphism.
\end{cor}
\begin{proof} 
	To see that $p_*$ is a monomorphism (i.e., that is is injective), it suffices to show that $\ker p_*$ is trivial.\\
	Let $[\sigma] \in \pi_1(E, e_0)$ be an element of $\ker p_*.$\\
	Then, $\sigma$ is a loop at $e_0$ in $E$ such that $p \circ \sigma$ is a loop at $x_0$ such that
	\begin{equation*} 
		p\circ \sigma \simeq e_{x_0} \rel \{0, 1\}.
	\end{equation*}
	(Where $e_{x_0}$ denotes the constant loop as usual.)\\
	Lifting them back and using the previous theorem, we see that
	\begin{equation*} 
		\sigma \simeq e_{e_0} \rel \{0, 1\}. \qedhere
	\end{equation*}
\end{proof}

Note that if $\sigma$ is a loop at $x_0$ in $X,$ its lifting $\sigma_{e_0}'$ in $X$ need not be a loop at $e_0.$ (For example, consider $(\mathbb{R}, 0) \overset{p}{\longrightarrow} (S^1, (1, 0))$ given by $p(x) = e^{2\pi ix}.$ The lift of the loop $\sigma$ in $S^1$ given by $s \mapsto e^{2\pi is}$ is the loop $\sigma_0'$ in $\mathbb{R}$ given by $s \mapsto s,$ which ends at $1.$)\\~\\
However, its terminal point will be a point in $p^{-1}(x_0).$ Moreover, as we saw earlier, the endpoint only depends on the homotopy class of the loop. Thus, we get a well-defined operation
\begin{equation*} 
	\cdot:p^{-1}(x_0) \times \pi_1(X, x_0) \to p^{-1}(x_0)
\end{equation*}
given by
\begin{equation*} 
	e\cdot[\sigma] = \sigma_e'(1).
\end{equation*}
\begin{prop}[$\cdot$ is a group action]
	The above operations satisfies the following properties:
	\begin{enumerate}
		\item $e\cdot 1 = e$ for all $e \in p^{-1}(x_0),$
		\item $e\cdot([\sigma]*[\tau]) = (e \cdot [\sigma])\cdot[\tau]$ for all $e \in p^{-1}(x_0)$ and all $\sigma, \tau \in \pi_1(X, x_0).$
	\end{enumerate}
\end{prop}
Thus, the above $\cdot$ is a \emph{right group action.}
\begin{proof} 
	Let $e \in p^{-1}(x_0),$ $[\sigma], [\tau] \in \pi_1(X, x_0)$ be arbitrary.
	\begin{enumerate}
		\item Note that $1 \in \pi_1(X, x_0)$ is simply the class of the constant loop $[e_{x_0}].$\\
		The lift of the constant loop is again a constant loop. Thus, since $1_e'$ starts at $e,$ it must end at $e$ as well. In other words,
		\begin{equation*} 
			e = 1_e'(1) = e\cdot 1,
		\end{equation*}
		as desired.
		\item Define $c \in p^{-1}(x_0)$ as $c \vcentcolon= \sigma_e'(1) = e\cdot[\sigma].$\\
		We wish to show that
		\begin{equation*} 
			e\cdot([\sigma*\tau]) = (e \cdot [\sigma])\cdot[\tau].
		\end{equation*}
		In other words, we wish to show that
		\begin{equation*} 
			(\sigma*\tau)_e'(1) = \tau_c'(1).
		\end{equation*}
		Consider the path $\sigma_e'*\tau_c'$ in $E.$ The product is well defined since $\sigma_e'(1) = c = \tau_c'(0).$\\
		Now, observe that

		\begin{align*} 
			p(\sigma_e'*\tau_c')(s) &= \begin{cases}
				p(\sigma_e'(2s)) & 0 \le 2s \le 1,\\
				p(\tau_c'(2s - 1)) & 1 \le 2s \le 2
			\end{cases}\\
			&= \begin{cases}
				\sigma(2s) & 0 \le 2s \le 1,\\
				\tau(2s - 1) & 1 \le 2s \le 2
			\end{cases}\\
			&= (\sigma*\tau)(s).
		\end{align*}
		In other words, $\sigma_e'*\tau_c'$ is a lift of $\sigma*\tau$ with initial point $e.$ By uniqueness of lifts, we see that
		\begin{equation*} 
			(\sigma*\tau)_e' = \sigma_e'*\tau_c'.
		\end{equation*}
		Thus, we see that
		\begin{equation*} 
			(\sigma*\tau)_e'(1) = \sigma_e'*\tau_c'(1) = \tau_c'(1),
		\end{equation*}
		as desired. \qedhere
	\end{enumerate}
\end{proof}
\begin{prop}[Description of stabilisers]
	The stabiliser of a point $e_0 \in p^{-1}(x_0)$ is the subgroup 
	\begin{equation*} 
		p_*\pi_(E, e_0) \subset \pi_1(X, x_0).
	\end{equation*}
\end{prop}
\begin{proof} 
	Note that $[\sigma] \in \pi_1(E, x_0)$ belongs to the stabiliser $S$ of $e_0$ iff $\sigma_{e_0}'(1) = e_0.$\\
	In other words, $[\sigma] \in S$ iff $\sigma$ lifts to a loop at $e_0.$\\
	If $\sigma = p \circ \sigma'$ for some loop $\sigma'$ at $e_0,$ then $[\sigma] \in S.$\\
	Conversely, if $[\sigma] \in S,$ then $\sigma_{e_0}'(1) = e_0$ and thus, $[\sigma_{e_0}'] \in \pi_1(E, e_0)$ with $\sigma = p \circ \sigma_{e_0}'.$
\end{proof}

\begin{prop}
	If $E$ is pathwise connected, $\pi_1(X, x_0)$ acts transitively.
\end{prop}
\begin{proof} 
	Let $e, c \in p^{-1}(x_0).$ We wish to show that there exists $[\sigma] \in \pi_1(X, x_0)$ such that $e\cdot[\sigma] = c.$\\
	Since $E$ is pathwise connected, we can find a path $\sigma'$ in $E$ from $e$ to $c.$ Then, $\sigma = p \circ \sigma'$ fits the bill.\\
	To see this, note that $\sigma'$ is indeed the lift of $\sigma$ with initial point $\sigma.$ That is, $\sigma' = \sigma_e'.$ Moreover, since it ends at $c,$ we get
	\begin{equation*} 
		e\cdot[\sigma] = \sigma_e'(1) = \sigma'(1) = c. \qedhere
	\end{equation*}
\end{proof}

Recall from group theory that given an action $\cdot:S \times G \to S$ with $s_0\cdot g = s_1,$ we have $G_{s_0} = gG_{s_1}g^{-1},$ where $G_s$ denotes the stabiliser of $s$ in $G.$\\
Thus, if $E$ is pathwise connected, then all the different subgroups $p_*\pi_1(E, e)$ are conjugate, as $e$ runs over all points in $p^{-1}(x_0).$

\begin{cor}
	If $E$ is pathwise connected, the map $[\sigma] \mapsto e_0\cdot[\sigma]$ induces a bijection of the set of all cosets $p_*\pi_1(E, e_0)[\sigma]$ onto the fiber. In particular, if $p^{-1}(x_0)$ is finite, the number of points in the fiber is equal to the index of the subgroup $p_*\pi_1(E, e_0).$
\end{cor}
\begin{proof} 
	In general, let $\cdot:S \times G \to S$ be a group action.\\
	Let $G_s \le G$ be the stabiliser of $s \in S.$\\
	Then, given any $g, ' \in G$ we have
	\begin{equation*} 
		s\cdot g = s\cdot g'
	\end{equation*}
	iff
	\begin{equation*} 
		g\cdot g'^{-1} \in G_s \text{ or } g \in G_sg'.
	\end{equation*}
	Thus, the map $G/G_s \to S$ given by
	\begin{equation*} 
		G_sg \mapsto s\cdot g
	\end{equation*}
	is well defined and an injection.\\
	Moreover, if the action is transitive, then the above map is clearly surjective as well.\\
	(In the above, $G/G_s$ is just the \emph{set} of right cosets, no assumptions of normality.) 
\end{proof}

\begin{defn}[Group of covering transformations]
	Given a covering space $E \overset{p}{\longrightarrow} X,$ the group $G$ of \emph{covering transformations} is the group of all homeomorphisms of $E$ which preserves the fibers, that is, all those $\varphi$ such that $p\varphi = p.$

	\begin{center}
		\begin{tikzcd}
			{E} \arrow[rr, "\varphi"]\arrow[rdd, "p"'] && {E} \arrow[ldd, "p"]\\
			&&\\
			& X &
		\end{tikzcd}
	\end{center}
\end{defn}

\begin{thm}
	Given a covering space $(E, e_0) \overset{p}{\longrightarrow} (X, x_0)$ with group of covering transformation $G.$ If $E$ is simply connected and locally pathwise connected, $G$ is canonically isomorphic to $\pi_1(X, x_0).$
\end{thm}
This achieves the result we described at the beginning of the section.
\begin{proof} 
	First, we define a homomorphism 
	\begin{equation*} 
		\chi:G \to \pi_1(X, x_0).
	\end{equation*}
	Let $\varphi \in G.$ Since $E$ is simply connected, all paths from $e_0$ to $\varphi(e_0)$ are homotopic relative $\{0, 1\}.$ (By \cref{lem:simpconnpathshomot}.)\\
	Thus, if $\sigma'$ is such a path, then $p_*([\sigma'])$ depends only on $e_0$ and $\varphi(e_0);$ we define
	\begin{equation*} 
		\chi(\varphi) = [p \circ \sigma'].
	\end{equation*}
	(That is, we define $\chi(\varphi)$ to be $p_*([\sigma'])$ for any path $\sigma'$ from $e_0$ to $\varphi(e_0).$ Note that $e_0$ is fixed.)\\
	Note that since $p\varphi = p,$ we see that $p(\varphi(e_0)) = p(e_0) = x_0$ and hence, $p\circ \sigma'$ is indeed a \emph{loop} at $x_0.$ Thus, the above map $\chi$ indeed is a map from $G$ to $\pi_1(X, x_0).$\\
	
	\begin{blockquote}
		\textbf{Claim 1.} $\chi$ is a homomorphism.
		\begin{proof} 
			Let $\varphi, \psi \in G.$ Let $\sigma'$ be any path from $e_0$ to $\varphi(e_0)$ and $\tau'$ be any path from $e_0$ to $\psi(e_0).$\\
			Define the path $\alpha' = \psi\circ\sigma'.$ This is clearly a path from $\psi(e_0)$ to $\psi(\varphi(e_0)).$ In particular, $\tau'*\beta'$ is a path from $e_0$ to $\psi(\varphi(e_0)).$ \\
			Moreover, since $\psi \in G,$ we have
			\begin{equation*} 
				p\circ\alpha' = p\circ\psi\circ\sigma' = p\circ\sigma'.
			\end{equation*}
			Thus, we have
			\begin{align*} 
				\chi(\psi\circ\varphi) &= [p\circ(\tau'*\alpha')]\\
				&=[p\circ\tau']*[p\circ\alpha']\\
				&=[p\circ\tau']*[p\circ\sigma']\\
				&=\chi(\psi)*\chi(\varphi). \qedhere
			\end{align*}
		\end{proof}
	\end{blockquote}

	\begin{blockquote}
		\textbf{Claim 2.} $\chi$ is injective.
		\begin{proof} 
			By definition, it is clear that 
			\begin{equation*} 
				\varphi(e_0) = e_0\cdot\chi(\varphi).
			\end{equation*}
			Hence, $\chi(\varphi) = 1$ implies that $\varphi(e_0) = e_0\cdot1 = e_0,$ i.e., $\varphi$ fixes $e_0.$\\
			However, note that being a covering transformation, we have that $p\varphi = p;$ in other words, $\varphi$ lifts $p.$ By \ref{thm:uniquelift}, there is only one lift of $p$ which fixes $e_0.$ Since the identity is one such, we see that $\chi(\varphi) = 1 \implies \varphi = \id,$ the identity of $\pi_1(X, x_0),$ proving that $\chi$ is injective. 
		\end{proof}
	\end{blockquote}

	\begin{blockquote}
		\textbf{Claim 3.} $\chi$ is surjective.
		\begin{proof} 
			Let $[\sigma]\in\pi_1(X, x_0)$ be arbitrary. We construct a $\varphi \in G$ such that $\chi(\varphi) = [\sigma].$\\
			We define $\varphi$ as follows:\\
			Let $e \in E,$ let $\tau'$ be any path from $e_0$ to $e,$ and let $\tau = p\circ\tau'.$ Note that $\tau$ is a path from $p(e_0) = x_0$ to $p(e) =\vcentcolon x.$ Then, $\tau^{-1}\sigma\tau$ is a loop at $x.$ We define
			\begin{equation*} 
				\varphi(e) \vcentcolon= e\cdot[\tau^{-1}\sigma\tau],
			\end{equation*}
			where the $\cdot$ is as before. (The endpoint of the unique lift of $\tau^{-1}\sigma\tau$ in $E$ starting at $e.$)\\
			Note that the above does not depend on $\tau'$ since $E$ is simply connected. (As earlier, we use \cref{lem:simpconnpathshomot}.)\\
			In other words, $\varphi$ just depends on $[\sigma].$\\
			Now, taking $e = e_0,$ we may take $\tau'$ as the constant map and we see that $\varphi(e_0) = e_0\cdot[\sigma] = \sigma_{e_0}'(1).$\\
			Thus, to compute $\chi(\varphi)$ using the definition of $\chi,$ we may take the path joining $e_0$ and $\varphi(e_0)$ to be $\sigma_{e_0}'$ and we get
			\begin{equation*} 
				\chi(\varphi) = [p \circ \sigma_{e_0}'] = [\sigma],
			\end{equation*}
			as would be desired. Thus, we just need to show that $\varphi \in G.$\\~\\
			It is easy to see that that $p\varphi = p.$ Indeed, since $\varphi(e)$ is the endpoint of a lift of a \emph{loop} at $p(e),$ we see that that it must belong to the fiber $p^{-1}(x).$ Thus, $p(\varphi(e)) = x = p(e).$\\
			Moreover, $\varphi$ has an inverse of the same type that is obtained by replacing $\sigma$ with $\sigma^{-1}$ in the definition. Thus, we just need to show that $\varphi$ is continuous. (The same will show that $\varphi^{-1}$ is also continuous.)\\~\\
			To do so, we will show the following: For every $e_1 \in E$ and every neighbourhood $V'$ of $\varphi(e_1),$ there exists a neighbourhood $V$ of $e_1$ such that $\varphi(V) \subset V'.$\\
			To this end, let $e_1 \in E$ be arbitrary. Consider $x_1 = p(e_1) \in X.$\\
			Let $U$ be an open neighbourhood of $x_1$ which is evenly covered. Since $E$ is locally pathwise connected, so is $X$ and thus, we may assume so is $U.$ (Or we replace $U$ by a smaller pathwise connected neighbourhood, which will still be evenly covered.)\\
			Then, $e_1 \in S_1$ and $\varphi(e_1) \in S_1'$ for some sheets $S_1, S_1'$ over $U.$ (Recall that $e_1$ and $\varphi(e_1)$ belong to the same fiber $p^{-1}(x_1).$) \\
			We claim that $\varphi(S_1) \subset S_1'.$ \\
			To see this, note that if $e \in S_1,$ we can join $e_1$ to $e$ by some path $\alpha'$ in $S_1$ (since $E$ is locally pathwise connected); then, consider the path $p\circ \tau$ in $X$ from $x_1$ to $p(e);$ lifting this to a path $\tau_{\varphi(e_1)}',$ we see that it is in $S_1'.$ In particular, its end point is a point in $S_1'.$ This end point is just $\varphi(e).$ Thus, we have that shown $\varphi(e) \in S_1'$ or that $\varphi(S_1) \subset S_1'.$\\~\\
			Now, given any neighbourhood $V'$ of $\varphi(e_1),$ we can find a neighbourhood $S_1' \subset V'$ of $\varphi(e_1)$ of the above type. (That is, a neighbourhood of $\varphi(e_1)$ which is a sheet over some open neighbourhood $U$ of $x_1 \in X.$)\\
			This proves that $\varphi$ is continuous and thus, $\varphi \in G.$
		\end{proof}
	\end{blockquote}
	With that, we are done!
\end{proof}
\end{document}