\documentclass[12pt,oneside]{book}
\usepackage{amsmath, amssymb, amsfonts, amsthm, mathtools}
\usepackage{thmtools}
\usepackage{witharrows}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage[colorlinks=true]{hyperref}
\usepackage{parskip}
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows.meta}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}
\numberwithin{thm}{chapter}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{defn}[thm]{Definition}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{ex}[thm]{Example}
\newtheorem{rem}[thm]{Remark}


\setlength\parindent{0pt}

\let\emptyset\varnothing

\pagestyle{plain}

\usepackage{titlesec}
\titleformat{\section}[block]{\sffamily\Large\filcenter\bfseries}{\S\thesection.}{0.25cm}{\Large}
\titleformat{\subsection}[block]{\large\bfseries\sffamily}{\S\S\thesubsection.}{0.2cm}{\large}

\usepackage[a4paper]{geometry}
\usepackage{lipsum}

\usepackage{cleveref}
\crefname{thm}{theorem}{theorems}
\crefname{lem}{lemma}{lemmas}
\crefname{defn}{definition}{definitions}
\crefname{prop}{proposition}{propositions}
\crefname{cor}{corollary}{corollaries}
\crefname{ex}{example}{examples}
\crefname{rem}{remark}{remarks}
\crefname{equation}{}{}

\newcommand{\downsym}{[$\downarrow$]}
\newcommand{\upsym}{[$\uparrow$]}

\usepackage{mdframed}
\newenvironment{blockquote}
{\begin{mdframed}[skipabove=0pt, skipbelow=0pt, innertopmargin=4pt, innerbottommargin=4pt, bottomline=false,topline=false,rightline=false, linewidth=2pt]}
{\end{mdframed}}

\renewcommand{\familydefault}{\sfdefault}

\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\sffamily{\S\textbf{\nouppercase{\rightmark}}}}
\fancyhead[R]{\sffamily{\thepage}}

\newcommand{\deff}[1]{{\color{blue}#1}}
\newcommand{\md}[1]{{\left\lvert #1 \right\lvert}}
\newcommand{\andd}{\quad\text{and}\quad}
\newcommand{\forward}{($\Rightarrow$)\ }
\newcommand{\backward}{($\Leftarrow$)\ }

\DeclareMathOperator{\chr}{char}
\DeclareMathOperator{\Frac}{Frac}
\DeclareMathOperator{\irr}{irr}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\disc}{disc}
\DeclareMathOperator{\D}{D}

\title{MA-414\\Galois Theory}
\author{Aryaman Maithani\\\url{https://aryamanmaithani.github.io/}}
\date{Last updated: \today}

\begin{document}
\maketitle
\tableofcontents
\setcounter{chapter}{-1}
\input{chapters/00}
\input{chapters/01}
\input{chapters/02}
\input{chapters/03}
\input{chapters/04}

\section{Finite fields}

\section{Existence and Uniqueness}

In this section, $p$ will denote an arbitrary prime number.

\begin{restatable}[Uniqueness of finite fields]{thm}{uniquefinfields}
\label{thm:uniquefinfields}
    Let $\mathbb{K}$ and $\mathbb{L}$ be finite fields with same cardinality. Then, $\mathbb{K}$ and $\mathbb{L}$ are isomorphic. \hfill\hyperref[thm:uniquefinfields2]{\downsym}
\end{restatable}

\begin{defn}%[]
    We shall denote the finite with $p^n$ elements by $\mathbb{F}_{p^n}.$
\end{defn}

\begin{rem}
    We have not yet shown that $\mathbb{F}_{p^n}$ for every prime $p$ and $n \in \mathbb{N}.$ Have only shown uniqueness up to isomorphism.
\end{rem}

\begin{restatable}[Existence of finite fields]{thm}{existencefinfields}
\label{thm:existencefinfields}
    Fix a prime $p$ and an algebraic closure $\overline{\mathbb{F}}_p.$ For every $n \in \mathbb{N},$ there exists a unique subfield of $\overline{\mathbb{F}}_p$ of size $p^n,$ denoted $\mathbb{F}_{p^n}.$ Moreover
    \begin{equation*} 
        \overline{\mathbb{F}}_p = \bigcup_{n \in \mathbb{N}} \mathbb{F}_{p^n}.
    \end{equation*}
    \hfill\hyperref[thm:existencefinfields2]{\downsym}
\end{restatable}

\section{Gauss' Necklace Formula}

Recall the M\"obius inversion formula.

\begin{defn}%[]
    The \deff{M\"obius function} $\mu : \mathbb{N} \to \mathbb{N}$ is defined as
    \begin{equation*} 
        \mu(n) \vcentcolon= \begin{cases}
            1 & n = 1,\\
            (-1)^r & n \text{ is a product of }r \text{ distinct primes},\\
            0 & p^2 \mid n \text{ for some prime }p.
        \end{cases}
    \end{equation*}
\end{defn}

\begin{thm}[M\"obius inversion formula]
    Let $f, g : \mathbb{N} \to \mathbb{N}$ be functions satisfying
    \begin{equation*} 
        f(n) = \sum_{d \mid n} g(d).
    \end{equation*}
    Then, they also satisfy
    \begin{equation*} 
        g(n) = \sum_{d \mid n} f\left(\frac{n}{d}\right)\mu(d).
    \end{equation*}
\end{thm}

\begin{restatable}[Gauss]{thm}{gaussnecklace}
\label{thm:gaussnecklace}
    The number of irreducible polynomials of degree $n$ over $\mathbb{F}_{q}$ is given by
    \begin{equation*} 
        N_q(n) = \frac{1}{n}\sum_{d \mid n} \mu(d)q^{n/d}.
    \end{equation*} \hfill\hyperref[thm:gaussnecklace2]{\downsym}
\end{restatable}

\gaussnecklace*\label{thm:gaussnecklace2}
\begin{flushright}\hyperref[thm:gaussnecklace]{\upsym}\end{flushright}
\begin{proof}
    
\end{proof}

\input{proofs}

\uniquefinfields*\label{thm:uniquefinfields2}
\begin{flushright}\hyperref[thm:uniquefinfields]{\upsym}\end{flushright}
\begin{proof}
    Let $q \vcentcolon= \md{\mathbb{K}}$ and $p \vcentcolon= \chr(\mathbb{K}).$ Then, $q = p^n$ for some $n \in \mathbb{N}.$ Note that $\mathbb{K}^\times$ is a group of order $q - 1.$ By Lagrange's theorem, we have $a^{q - 1} = 1$ for all $a \in \mathbb{K}^\times.$ In turn, we get $a^q - a = 0$ for \emph{all} $a \in \mathbb{K}.$

    Hence, $\mathbb{K}$ is a splitting field of $x^q - x$ over $\mathbb{F}_p$ and so is $\mathbb{L}.$ By \Cref{thm:isosplitting}, $\mathbb{K}$ and $\mathbb{L}$ are isomorphic.
\end{proof}

\existencefinfields*\label{thm:existencefinfields2}
\begin{flushright}\hyperref[thm:existencefinfields]{\upsym}\end{flushright}
\begin{proof}
    Fix $n \in \mathbb{N}$ and let $q = p^n.$ $\overline{\mathbb{F}}_p$ contains a unique splitting field of $x^q - x =\vcentcolon f(x)$ over $\mathbb{F}_p.$ We show that this splitting field has $q$ elements. Consider
    \begin{equation*} 
        \mathbb{K} = \{\alpha \in \overline{\mathbb{F}}_p \mid f(\alpha) = 0\}.
    \end{equation*}
    Then, $\md{\mathbb{K}} = q$ since $f(x)$ is separable, by \Cref{thm:derivcritsep}. 

    Thus, $\mathbb{K}$ is the desired splitting field. Conversely any other field with $q$ elements would be the set of roots of $x^q - x$ and hence, we have uniqueness.

    We now show that $\overline{\mathbb{F}}_p = \bigcup_{k \ge 1}\mathbb{F}_{p^k}.$ Let $\alpha \in \overline{\mathbb{F}}_p$ and let $d \vcentcolon= \deg_{\mathbb{F}}(\alpha).$ Then, $[\mathbb{F}(\alpha) : \mathbb{F}] = d$ and hence, $\alpha \in \mathbb{F}(\alpha) = \mathbb{F}_{p^d}.$
\end{proof}
\end{document}